% Template for B. Sc and M. Sc. (Tech.) degree programmes at the
% Faculty of Information Technology and Electrical Engineering
% at University of Oulu (CSE/BME/BA)
%
% Authors: Mika Korhonen (original author), Pekka Pietikäinen, Christian Wieser, Teemu Tokola, Juha Kylmänen, Tuomas Holmberg and Tuomas Varanka.
% If you make any improvements to this template, submit them via
% https://github.com/ouspg/cse-thesis
%
% Signing in to Overleaf with a oulu.fi account is strongly recommended, this gives students and staff
% access to a Professional subscription
%
% CHANGELOG
% 2023-01-31: Track changes has been turned on - TTo
% 2023-06-15: Improvements to avoid missing filling in some details: TODO's added to template (TTo)
% 2023-06-15: Changes to foreword, clarifications to indicate template is also for Bachelor thesis  (TTo)
% 2023-06-15: Example of a CC-BY figure added with reference in the footnotes (TTo)
% 2025-08-18: Major refactoring of the template (PPi)

%
% dithesis.cls supports the following options
% Language: english/finnish
% Degree programme: cse (default)/bme/ba
% Thesis type: master (default)/bachelor
% Output type: online (default, 2.5 cm margin)
%              print (4.5 cm left margin for bound theses)
\documentclass[english, online, cse, master]{dithesis}

%% Copyright of a work is with the creator/author of the work regardless of
%% whether the copyright mark is explicitly in the work or not. You may, if you
%% wish---we encourage you to do so---publish your work under a Creative
%% Commons license (see creativecommons.org), in which case the license text
%% must be visible in the work.

% Uncommenting one of the following will automatically create a copyright page
% If both are commented out the license is "All rights reserved"
% and no copyright page will be generated
%
%\input{copyright-allrightsreserved}
\input{copyright-ccby40.tex}

% TikZ for the architecture diagram in Chapter 3.
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric}

% tcolorbox for the per-hypothesis verdict blocks in Chapter 4.
\usepackage[most]{tcolorbox}

%%%%%%%%%%%%%%%%%%%%% SET YOUR INFORMATION HERE %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Both English and Finnish title are needed
\title{Memory Bus for Multi-Fragment LLM Workflows: Context Compression, the Coordination Cliff, and Privacy}
\otsikko{Muistiv\"ayl\"a monifragmenttisille kielimallity\"onkuluille: kontekstin tiivist\"aminen, koordinaation jyrk\"anne ja yksityisyys}

\firstname{Syed Abdullah}
\lastname{Hassan}

% Names of other authors can be added here
%\firstnametwo{}
%\lastnametwo{}
%\firstnamethree{}
%\lastnamethree{}
% Remove or comment the extra names if you do not need them

% Abstracts are stored in the PDF metadata.
% They must not contain empty lines (multiple paragraphs) or special
% characters. Mathematical symbols should work (mathxmp option of the pdfx
% package).
% If the abstract contains multiple paragraphs or special characters,
% provide the full text in abstract.tex and tiivistelma.tex.
% This version should otherwise remain identical to it
\abstract{Large language models running in multi-step workflows pay
  for every token they read. Context compression is the natural lever,
  yet the single-agent prompt-compression literature does not measure
  whether the compression that preserves question-answering accuracy
  also preserves the harder property a planner needs: combining
  information distributed across several fragments into a correct
  answer. This thesis studies that question on multi-fragment LLM
  workflows. The evaluation uses either a deterministic regex parser
  or a single LLM call with all (compressed) fragments visible as the
  planner; multi-round agent simulation is outside the empirical
  scope. Four contributions are delivered. A reproducible
  coordination benchmark of 150 instances across three workload
  families. An empirical characterisation of the coordination cliff
  with a compounding-error model that predicts its position from
  per-round token recall, cross-architecture validated on Qwen-72B
  and DeepSeek V4 Pro within a calibrated regime. A catalogue of
  three RAG pipelines showing compress-first is robustly preferred
  in both storage- and accuracy-bounded regimes. A memory-bus
  reference implementation and a summary-level inference-disclosure
  metric. Headline verdicts: question-answering accuracy decorrelates
  from coordination success; a sharp cliff exists; planner capacity
  sets the success ceiling, not the cliff position, within the
  calibrated regime; information density scales the cliff across
  datasets; and compression measurably reduces protected-fact
  disclosure. A cliff-aware adaptive wrapper, CAAC, operationalises
  the compounding-error bound as a runtime back-off.}

\tiivistelma{Monitoimijallisissa ja monivaiheisissa
  ty\"onkulkutilanteissa toimivat suuret kielimallit maksavat
  jokaisesta lukemastaan merkist\"a. Kontekstin tiivist\"aminen on
  luonteva keino, mutta yksitoimijallinen tiivistyskirjallisuus ei
  mittaa, s\"ailytt\"a\"ak\"o kysymys-vastaus-tarkkuutta s\"ailytt\"av\"a
  tiivist\"aminen my\"os vaikeamman ominaisuuden: kyvyn yhdist\"a\"a
  useaan tietoaineistoon hajautettu tieto oikeaksi vastaukseksi.
  T\"am\"a diplomity\"o tutkii t\"at\"a kysymyst\"a
  monifragmenttisissa kielimallity\"onkuluissa. Arvioinnissa
  k\"aytet\"a\"an joko deterministist\"a s\"a\"ann\"ollisten lausekkeiden
  j\"asent\"aj\"a\"a tai yht\"a kielimallikutsua, jossa kaikki
  tiivistetyt fragmentit ovat n\"akyviss\"a; monikierroksinen
  agenttisimulaatio on empiirisen tarkastelun ulkopuolella. Ty\"on
  kontribuutiot ovat (i) toistettavissa oleva koordinaatiokokoelma,
  jossa on 150 instanssia kolmesta ty\"okuormaperheest\"a; (ii)
  empiirinen luonnehdinta koordinaatiojyrk\"anteest\"a ja siihen
  liittyv\"a yhdist\"av\"a-virhe-malli, joka ennustaa jyrk\"anteen
  paikan per-kierroksisesta token-saannista, validoitu Qwen-72B- ja
  DeepSeek V4 Pro -malleilla kalibroidulla alueella; (iii) kolmen
  RAG-putken katalogi, joka osoittaa ett\"a tiivist\"a-ensin on
  vakaasti suositeltava molemmissa, sek\"a tallennustila- ett\"a
  tarkkuusrajoitetuissa olosuhteissa; ja (iv) muistiv\"aylan
  viiteimplementaatio sek\"a yhteenvetotason
  p\"a\"attelyilmaisumetriikka. P\"a\"atulokset: kysymys-vastaus-
  tarkkuus dekorreloituu koordinaatiosta; jyrkk\"a koordinaatio-
  jyrk\"anne on olemassa; mallin kapasiteetti m\"a\"ar\"a\"a
  onnistumiskaton, ei jyrk\"anteen paikkaa, kalibroidulla alueella;
  informaatiotiheys skaalaa jyrk\"annett\"a aineistojen v\"alill\"a;
  ja tiivist\"aminen v\"ahent\"a\"a mitattavasti suojattujen
  faktojen vuotamista. Soviteltava tiivistys (CAAC) realisoi
  yhdist\"av\"an-virheen rajan ajonaikaiseksi turvarajaksi.}

% Keywords are also included in the PDF metadata, and cannot contain any
% special characters. Separate them with \spc
\keywords{context compression\spc large language models\spc coordination cliff\spc multi-fragment workflows\spc memory bus\spc inference disclosure\spc agentic memory\spc retrieval-augmented generation}
\avainsanat{kontekstin tiivist\"aminen\spc suuret kielimallit\spc koordinaatiojyrk\"anne\spc monifragmenttiset ty\"onkulut\spc muistiv\"ayl\"a\spc p\"a\"attelyilmaisu\spc agenttinen muisti\spc hakuparannettu generointi}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \headertitlecap automatically creates headers with TitleCaps
% (Capitalizes the First Letter in Each Word except ``Small'' Ones)
% https://en.wikipedia.org/wiki/Title_case
% This only has effect in English. In Finnish headers follow
% the normal Finnish rules of capitalization.
%
% Title (abstract page, on front page it is all caps)
% Chapters are all caps
% Sections are title case
% Subsections are title case
% Subsubsections are in sentence case (as in IEEE Style manual)
% Words not to be capitalized can be changed in dithesis.sty.
%
% Note that this does not affect the PDF table of contents, which is stored
% in the metadata.
% Because of this, you should consistently capitalize headers in your .tex
% Both normal (sentence) case and title case are acceptable.
% This template uses sentence case.
\headertitlecap

% Add your bibliographies here. You can use several with BibLaTeX.
\addbibresource{citations.bib}

\begin{document}
\pagestyle{empty}
\maketitlepage
\makecopyrightpage

\IfLang{\MainLang}{finnish}{
  \input{Chapters/tiivistelma}
  \input{Chapters/abstract}
  \selectlanguage{finnish}
} {
  \input{Chapters/abstract}
  \input{Chapters/tiivistelma}
  \selectlanguage{english}
}

\contents %Insert table of contents
\input{Chapters/foreword}
\input{Chapters/abbreviations}

% Enables page numbers and sets the dots for numbered chapters in
% table of contents
\mainmatter

\chapter{Introduction}
  \label{introduction}
  \input{Chapters/introduction}

\chapter{Background and Related Work}
  \label{relatedwork}
  \input{Chapters/relatedwork}

\chapter{System Design and Implementation}
  \label{implementation}
  \input{Chapters/implementation}

\chapter{Experiment Design and Protocol}
  \label{experiments}
  \input{Chapters/experiments}

\chapter{Discussion and Summary}
  \label{summary}
  \input{Chapters/summary}

\printbibliography[heading=bibnumbered, title=\mybibname]

\startappendix
\chapter{Appendices}
  \label{appendix}
  \input{Chapters/appendices}

\end{document}
