\begin{thesisabstract}{english}
  \abstractmetadata

Large language models running in multi-step and multi-agent workflows
pay for every token they read. Energy, latency, and money scale with
context length, and a growing fraction of those tokens carry little
information --- conversational filler, repeated history, restated
system prompts. Context compression is the natural lever. The
single-agent prompt-compression literature is mature; what has not yet
been measured is whether compression that preserves single-agent
question-answering accuracy also preserves the harder property a
planner needs: combining information distributed across multiple
fragments into a correct answer.

This thesis studies that question on \emph{multi-fragment LLM
workflows}. The empirical evaluation uses either a deterministic
regex parser or a single LLM call with all (compressed) fragments
visible as the planner; multi-round agent simulation is outside the
empirical scope. Four contributions are delivered: (C1)~a
reproducible coordination benchmark of $150$ instances across three
workload families --- cross-document fact aggregation,
constraint-satisfaction planning, and multi-step retrieval; (C2)~an
empirical characterisation of the \emph{coordination cliff}
$\tau^{*}$ across four training-free compressors (LLMLingua-2,
Phi-3-Mini extractive, an instruction-aware filter, and a truncation
baseline), with a compounding-error model that predicts the cliff
position from per-round token recall and a cross-architecture
validation on Qwen-72B (within $0.8\%$ of the predicted position) and
DeepSeek V4~Pro (bootstrap confidence interval contains the
prediction) inside a formally-defined calibrated regime; (C3)~a
catalogue of three RAG pipelines showing that compress-first is
robustly preferred in both storage-bounded and accuracy-bounded
regimes, challenging the post-retrieval-compression assumption of the
LongLLMLingua line of work; and (C4)~a memory-bus reference
implementation built around a tamper-evident audit log and a
policy-aware compressor abstraction, together with a summary-level
\emph{inference-disclosure} metric that quantifies how compression
reduces the recoverability of protected facts to a downstream reader.

Five hypotheses are tested across approximately one hundred thousand
evaluation cells. H1 (single-agent question-answering accuracy
decorrelates from coordination success under compression) is
supported: Spearman~$\rho \in [-0.59, +0.38]$ across compressors,
with $95\%$~bootstrap confidence intervals excluding $0.6$. H2 (a
sharp cliff exists) is supported on eight of nine
(compressor,~family) cells with paired Wilcoxon $p < 0.0001$. The
original H5 is reframed and supported as \emph{Corollary~1
(ceiling--cliff separation)}: model capacity sets the success
ceiling $p_0$, not the cliff position $\tau^{*}$, within the
calibrated regime. The original H6 is reframed and supported as
\emph{Corollary~2 (information-density scaling)}: the cliff position
varies with task information density, with $\theta_\text{info}=0.97$
on a dense numeric-aggregation family and $0.37$--$0.48$ on
distributed multi-document benchmarks (HotpotQA and MultiHopRAG).
H4 (compression reduces inference disclosure) is supported with a
documented reader-bias caveat. The thesis also contributes
\emph{CAAC} --- a cliff-aware adaptive compression wrapper that
operationalises the compounding-error bound as a runtime back-off,
populating a complementary operating point on the
(coordination,~ratio) frontier.

The deliverable is the manuscript together with an open-source
reference implementation reproducible from a single command on
commodity hardware (Apple~M4 Pro 48~GB and an RTX~5090 32~GB
workstation for the GPU-bound sweeps).

\end{thesisabstract}
