This chapter specifies the experimental protocol for each of the eight
hypotheses, the metric suite, the statistical-analysis plan, and the
schedule of arms. Each hypothesis section gives the falsifiable claim
verbatim, the inputs the runner takes, the procedure, the decision rule
that maps the run's output to a verdict, and the wallclock estimate.
Result sections are explicit placeholders marked with the LaTeX comment
\verb|% RESULTS|: they will be populated by the experimental runs of
Months 3, 4, 6, 7, and 8 of the implementation plan and are
intentionally empty in this submission. The empirical findings will be
inserted into those slots verbatim from the
\texttt{results/h\{N\}/<run\_id>/} directory and the corresponding
\texttt{verdicts.json}.

\section{Metric Suite}
\label{sec:metric_suite}

The metric suite covers seven families. The first three are
quality-oriented and standard; the next two are coordination- and
compression-specific; the last two are operational.

\paragraph{Quality.} F1 (token-overlap), exact match (EM), ROUGE-L, and
BERTScore, all computed by pure-Python implementations against
ground-truth answers~\cite{rajpurkar2016squad, lin2004rouge,
zhang2020bertscore}. The F1 implementation matches the SQuAD reference,
which is the version reproduced by the LLMLingua-2 paper and the basis
for the calibration target.

\paragraph{Coordination.} Final task success, sub-task assignment
accuracy, rounds to completion, and critic-flagged error rate. All four
are pure functions of the workload and the trace, as documented in
Section~\ref{sec:c1} of Chapter~\charef{implementation}.

\paragraph{Faithfulness and hallucination.} RAGAS~\cite{ragas2023} and
DeepEval~\cite{deepeval2024} faithfulness scores, plus manual
annotation on a 100-example random sample for spot-check calibration.

\paragraph{Compression.} Input-to-output token ratio measured on
the wrapped tokenizer of the active compressor; total tokens per
workflow; per-stage compression ratio when more than one stage applies
(as in P2 and P3).

\paragraph{Cost.} EUR per query and EUR per workflow, computed from
the cost ledger using the pricing constants of Section~\ref{sec:rag_pipelines}
of Chapter~\charef{implementation}.

\paragraph{Latency.} p50 and p95 milliseconds per query, computed
separately for the compression step and end-to-end.

\paragraph{Governance.} Tag-preservation rate (per the H5 definition)
and inference-disclosure rate (per the H6 protocol).

\paragraph{LLM-as-judge.} A subset of metrics is scored by
GPT-4o-mini as the judge model, with a $10$\% sample cross-checked by
Claude Sonnet 4.6. Cohen's $\kappa$ below $0.85$ between the two
judges triggers a recalibration. The judge sees a position-randomised
pair of answers and never sees which compressor produced which answer.

\section{Statistical Analysis Plan}
\label{sec:stat_plan}

The pre-registered analysis plan is the one specified in the
implementation plan and the technical reference.

\paragraph{Seeds.} Five seeds per condition.

\paragraph{Confidence intervals.} Empirical 95\% bootstrap CI with
$10\,000$ resamples, computed via \texttt{bootstrap\_mean\_ci} in
\texttt{m6.evaluation.statistics}.

\paragraph{Paired comparisons.} For compressor-versus-compressor
comparisons on matched instances, the paired bootstrap. The
implementation uses the recentred-null percentile bootstrap p-value of
Efron and Tibshirani~\cite{efron1993bootstrap} (Chapter~16): a
two-sided test of $H_0$: mean difference $= 0$ is computed by
re-centring the bootstrap distribution around its own mean and
reporting the fraction of recentred bootstrap means whose absolute
value meets or exceeds the observed absolute mean.

\paragraph{Cliff-detection test (H2).} Mann--Whitney U for the
comparison of success-below-$\tau$ versus success-above-$\tau$. These
two samples are independent because they are drawn across different
$(\text{workload}, \text{seed}, \text{ratio})$ cells; a paired test
would be incorrect~\cite{mannwhitney1947, wilcoxon1945}.

\paragraph{Multiple-comparison correction.} Holm-Bonferroni within
each hypothesis family~\cite{holm1979bonferroni}. The families are
$\{H_1, H_2, H_3\}$, $\{H_4\}$, $\{H_5, H_6\}$, $\{H_7\}$, and
$\{H_8\}$.

\paragraph{Effect sizes.} Cliff's $\delta$ for ordinal
comparisons~\cite{cliff1993dominance} and Cohen's $d$ for continuous
ones, reported alongside p-values.

\paragraph{Validity.} Every experiment includes a no-compression
control condition. If the variance of the control on the metric of
interest meets or exceeds the variance of the treatment, the experiment
is flagged \texttt{invalid} in the run's manifest and the verdict is
suppressed. This is the documented mitigation for the AutoGen-runtime-bug
risk.

\section{Hypothesis H1 --- QA is a Poor Predictor of Coordination}
\label{sec:h1_design}

\paragraph{Falsifiable claim.} Spearman $\rho$ between the
single-agent QA-accuracy delta and the multi-agent
coordination-success delta across matched compression ratios is below
$0.6$ on at least two of the three compressors at 7B.

\paragraph{Inputs.} The C1 benchmark at version v0.1; the ICAE-style
trained compressor checkpoint; the MLX-LM backend at the 7B size.

\paragraph{Procedure.} For each
$(\text{compressor } c, \text{ratio } r, \text{workload } w,
\text{seed } s)$ cell: (i) build the single-agent QA derivative of
the workload (same sources, planner-only question, no workers or
critic) and record F1; (ii) run the planner-worker-critic loop and
record coordination success, sub-task accuracy, rounds, and
critic-flagged rate; (iii) compute
$\Delta_\text{qa} = qa(r) - qa(r{=}1)$ and
$\Delta_\text{coord} = \text{coord}(r) - \text{coord}(r{=}1)$. For
each compressor compute Spearman $\rho$ between
$\Delta_\text{qa}$ and $\Delta_\text{coord}$, with bootstrap CI.

\paragraph{Decision.} Supported if $\rho < 0.6$ on at least two of the
three compressors at 7B, with the bootstrap CI excluding $0.6$ from
above on the same two compressors. Falsified if $\rho \geq 0.6$ on at
least two compressors. Both verdicts are thesis-worthy.

\paragraph{Wallclock.} Approximately two days at 7B fp16.

% RESULTS: H1 results to be inserted from results/h1/7b/<run_id>/.

\section{Hypothesis H2 --- Coordination Cliff exists}
\label{sec:h2_design}

\paragraph{Falsifiable claim.} For each $(\text{compressor},
\text{workload})$ cell at 7B, there is a compression ratio $\tau^{*}$
such that coordination success at ratios $r > \tau^{*}$ falls by at
least 30\% relative to ratios $r < \tau^{*}$. $\tau^{*}$ varies by
workload but not by compressor family, within $\pm 20\%$.

\paragraph{Inputs.} The C1 benchmark, the three baseline compressors,
the MLX-LM backend at 7B and 13B (the latter on a 30-workload
sub-sample for sanity).

\paragraph{Procedure.} Sweep $r \in \{1, 2, 3, 4, 5, 6, 8, 10, 12, 16\}$
on each cell with five seeds. Fit a piecewise-linear function
$f(r; a, b, \tau)$ to the (ratio, success) curve via differential
evolution under the constraint that the right-piece slope is at most
the left-piece slope (the cliff drops). Run a Mann--Whitney U test on
success-below-$\tau$ versus success-above-$\tau$ with the
``greater'' alternative, then apply Holm correction within the
$\{H_1, H_2, H_3\}$ family.

\paragraph{Decision.} A cliff exists at a cell if the relative drop is
at least $0.30$ and the Holm-adjusted Mann--Whitney p-value is less
than $0.05$. The $\tau$-spread-by-workload check passes for a family
when the (max-min)/mean of $\tau^{*}$ across compressors is at most
$0.20$.

\paragraph{Wallclock.} Approximately 5--10 days at 7B plus 3 days at
13B sub-sample.

% RESULTS: H2 results, including the headline coordination-cliff figure,
%          to be inserted from results/h2/7b/<run_id>/ and 13b/<run_id>/.

\section{Hypothesis H3 --- Training Distribution Matters}
\label{sec:h3_design}

\paragraph{Falsifiable claim.} An ICAE-style compressor fine-tuned on
planner-worker-critic dialogue traces outperforms the same compressor
fine-tuned on monolithic QA, at matched single-agent QA accuracy.

\paragraph{Inputs.} Two ICAE checkpoints
(\texttt{icae-7b-qa} and \texttt{icae-7b-dialogue}) trained on
matched compute budgets (same optimiser, same LoRA configuration,
same step count) but on different datasets; the C1 family-(a)
workload subset.

\paragraph{Procedure.} For each checkpoint, sweep ratios and find the
operating ratio at which the two checkpoints' single-agent QA F1 are
within $\pm 1$~pp of each other (the matched operating point). At
that operating point, run the planner-worker-critic loop on the
C1 family-(a) workloads with the five seeds and compare coordination
success via the paired bootstrap.

\paragraph{Decision.} Supported if the paired bootstrap mean
$\text{coord}_\text{dialogue} - \text{coord}_\text{qa}$ is positive
and the Holm-adjusted p-value is less than $0.05$.

\paragraph{Wallclock.} Approximately two days; trainings can be
scheduled in parallel.

% RESULTS: H3 results to be inserted from results/h3/7b/<run_id>/.

\section{Hypothesis H4 --- RAG Pipeline Placement Matters}
\label{sec:h4_design}

\paragraph{Falsifiable claim.} P1 dominates P2 on storage-bounded
settings; P2 dominates P1 on accuracy-bounded settings; P3 closes the
gap on a combined accuracy-times-EUR score. Effect size of at least
5 pp F1.

\paragraph{Inputs.} The C1 family-(a) workloads plus NarrativeQA and
HotpotQA for external comparability; the three pipelines P1, P2, and
P3; the three compressors.

\paragraph{Procedure.} Two budget regimes are defined:
\textit{storage-bounded}, with the FAISS index size capped at 100~MB so
that both P1 and P2 are tuned to fit; and \textit{accuracy-bounded},
with retrieval recall@10 capped at $0.85$ so that both P1 and P2 are
tuned to meet that ceiling.
For each $(\text{pipeline}, \text{regime}, \text{ratio} \in
\{2, 4, 8\}, \text{seed})$ cell run the full workload and record
F1, EUR per query, latency p50 and p95, FAISS index megabytes, and
recall@10. P3 is swept over $(\theta_\text{high}, \theta_\text{low})$
on the small grid documented in
Section~\ref{sec:rag_pipelines} of Chapter~\charef{implementation}.

\paragraph{Decision.} P1-versus-P2 effect-size at least 5 pp F1 with
paired-bootstrap CI excluding $0$ in both regimes (with the sign
flipping per the H4 claim); P3 wins on a combined $F_1 / \text{EUR}$
ranking with Holm-adjusted p less than $0.05$.

\paragraph{Wallclock.} Approximately three days.

% RESULTS: H4 results, including the headline RAG-pipeline figure and
%          the EUR/workflow cost table, to be inserted from
%          results/h4/<run_id>/.

\section{Hypothesis H5 --- Tag Preservation}
\label{sec:h5_design}

\paragraph{Falsifiable claim.} At $4\times$ compression the tag
head preserves at least 85\% of fragment tags, with at most 5~pp
accuracy degradation relative to the unmodified baseline. The CI
lower bound on the accuracy delta is used as the strict test (not the
point estimate).

\paragraph{Inputs.} The ICAE baseline checkpoint and the C4
tag-preserving checkpoint; the C1 benchmark across the three tag
distributions (uniform, skewed, hierarchical).

\paragraph{Procedure.} For each $r \in \{2, 4, 8\}$ and each workload,
compress every fragment with the C4 variant and recover its tag via
the tag head. The preservation predicate combines the ACL test
(either the recovered ACL is a superset of the true ACL or the
intersection-over-true ratio is at least $0.9$) and the classification
test (the recovered classification is at least the true classification).
For the accuracy delta, run the planner-worker-critic loop with the
baseline and the C4 compressor on the same workloads with the same
seeds and compute the paired bootstrap of the coordination-success
difference.

\paragraph{Decision.} Supported if the mean preservation rate at
$4\times$ is at least $0.85$ and the paired-bootstrap CI lower bound on
the accuracy delta is at least $-5$~pp.

\paragraph{Wallclock.} Approximately one day.

% RESULTS: H5 results to be inserted from results/h5/<run_id>/.

\section{Hypothesis H6 --- Inference Disclosure}
\label{sec:h6_design}

\paragraph{Falsifiable claim.} A held-out reader recovers protected
facts from compressed summaries at a rate substantially above the
priors-only chance baseline when the tag-preserving compressor is
\emph{not} used (showing that the metric measures something real),
and at a lower rate when it \emph{is} used at matched compression.

\paragraph{Inputs.} The C1 fragments whose tag classification is at
least \textsc{confidential}; the protected-fact list shipped with
the benchmark (one or two yes/no questions per protected fragment with
ground-truth answers); the GPT-4o-mini API as the held-out reader.

\paragraph{Procedure.} Three conditions per workload. Under
\emph{priors only}, the reader sees only the workload's public
preamble, with no source fragments. Under \emph{baseline}, the reader
sees the compressed summary produced by the unmodified ICAE
compressor. Under \emph{C4}, the reader sees the compressed summary
produced by the tag-preserving variant at matched compression. The
reader answers each protected-fact question with yes/no/unknown, and
the recall of the protected facts is reported.

\paragraph{Decision.} The metric measures something real if
$\text{recall}_\text{baseline} > \text{recall}_\text{priors}$ with
paired-bootstrap p less than $0.05$. The C4 variant reduces disclosure
if $\text{recall}_\text{c4} < \text{recall}_\text{baseline}$ with
paired-bootstrap p less than $0.05$, both under Holm correction within
$\{H_5, H_6\}$.

\paragraph{Wallclock and cost.} Approximately one day; expected API
spend approximately EUR~30.

% RESULTS: H6 results to be inserted from results/h6/<run_id>/.

\section{Hypothesis H7 --- Model-Size Scaling of the Coordination Cliff}
\label{sec:h7_design}

\paragraph{Falsifiable claim.} Across $\{7\text{B}, 13\text{B},
34\text{B int4}, 70\text{B int4}\}$, $\tau^{*}$ increases monotonically
with model size on at least two of the three workload families. 70B
int4 is a single-point characterisation at the suspected $\tau^{*}$
identified at 13B/34B; 7B and 13B are full sweeps; 34B int4 is a
focused partial sweep.

\paragraph{Inputs.} The H2 machinery with the backend factory varied
across the four model sizes. The 70B GGUF Q4\_K\_M files are pulled via
the \texttt{download\_models.sh} script; the llama.cpp backend's
NarrativeQA-shaped sanity check is run at startup and the backend
refuses to serve if F1 drops by more than $5$~pp from the recorded
baseline.

\paragraph{Procedure.} (i) 7B full sweep, already collected for H2.
(ii) 13B full sweep on family (a) on a 30-workload sub-sample. (iii)
34B int4 focused sweep at $r \in \{\tau_\text{13B}-2,
\tau_\text{13B}, \tau_\text{13B}+2\}$ plus coarse sanity at
$r \in \{1, 16\}$ on 15 workloads. (iv) 70B int4 single point at
$r = \tau_\text{34B}$ with five seeds on 10 workloads, gated on the
sanity-check pass.

\paragraph{Decision.} Monotonically non-decreasing $\tau^{*}$ across
$\{7\text{B}, 13\text{B}, 34\text{B int4}, 70\text{B int4}\}$ on at
least two of three families; 70B is single-point on family (a) only.

\paragraph{Wallclock.} Approximately three weeks, dominated by the 70B
int4 throughput.

% RESULTS: H7 results, including the model-size scaling figure, to
%          be inserted from results/h7/{7b,13b,34b-int4,70b-int4}/.

\section{Hypothesis H8 --- Real-Trace Transfer}
\label{sec:h8_design}

\paragraph{Falsifiable claim.} On a subset of multi-agent workflows
reconstructed from real M0/M1/M2 traces, the qualitative shape of the
coordination-versus-compression curve matches synthetic results within
$\pm 15\%$ on $\tau^{*}$ and $\pm 10$ pp on coordination success.
Gated on M0/M1/M2 connector readiness.

\paragraph{Pre-condition.} The thesis ships with an
\texttt{docs/agent\_readiness.yaml} that records whether each of the
three sibling agents (Publication~DB / Contract~DB / Moodle--Patio) is
ready. The runner short-circuits with a \texttt{documented-as-deferred}
verdict if all three flags are \texttt{false}, per the scope-signoff
with the supervisor.

\paragraph{Procedure.} With the agent owners, identify two or three
cross-system workflows reconstructable from the trace exports.
Reformulate each as a \texttt{Workload} instance loadable by C1's
runner. Run the H2 procedure on those workflows. Compare $\tau^{*}$
and the coordination-success curve to the synthetic baseline.

\paragraph{Decision.} Supported if both $\tau^{*}$ and the
coordination-success curve are within the stated tolerances on at
least one workflow.

\paragraph{Wallclock.} Gated on connector readiness, not on compute.

% RESULTS: H8 results to be inserted from results/h8/<run_id>/, or the
%          deferred-arm statement from docs/agent_readiness.yaml if
%          no agent is ready by Month 7.

\section{Headline Figures}
\label{sec:figures}

The four chapter-headline figures the manuscript will produce are
listed in Table~\ref{tab:figures}; each figure is a single command
(\texttt{make reproduce-ch<N>}) that lands in
\texttt{results/h\{X\}/<run\_id>/plots/}.

\begin{table}[h]
\centering
\caption{Chapter-headline figures and their reproduction targets.}
\label{tab:figures}
\small
\begin{tabular}{p{1.5cm}p{6.5cm}p{6cm}}
\hline
Chapter & Figure & Reproduction \\
\hline
5 & Coordination cliff $\tau^{*}$ at 7B & \texttt{make reproduce-ch5} (H1, H2, H3) \\
6 & RAG pipeline placement and cost & \texttt{make reproduce-ch6} (H4) \\
7 & Tag preservation and inference disclosure & \texttt{make reproduce-ch7} (H5, H6) \\
8 & Model-size scaling of $\tau^{*}$ & \texttt{make reproduce-ch8} (H7) \\
\hline
\end{tabular}
\end{table}

% RESULTS-FIGURES: Insert the four headline figures here once the
%                  experimental runs have produced their CSVs and
%                  plot scripts.

\section{Threats to Validity}
\label{sec:threats}

\paragraph{Construct validity.}
The C1 benchmark is synthetic. The H8 arm is the construct-validity
check, and the documented-as-deferred path is the honest fallback if
M0/M1/M2 are not ready by Month~7.

\paragraph{Internal validity.}
The no-compression control condition guards against AutoGen-runtime
bugs confounding the compression-quality signal. The deterministic
backend provides a second upper bound that any AutoGen run must
match.

\paragraph{External validity.}
The 70B int4 single-point characterisation rests on the
NarrativeQA-shaped sanity check passing at startup. The H8 transfer
result, when available, anchors external validity against real
deployment traces.

\paragraph{Statistical validity.}
The recentred-null percentile-bootstrap p-value is more rigorous than
the tail-doubling shortcut and is consistent with the recommendations
of Efron and Tibshirani~\cite{efron1993bootstrap}. The Mann--Whitney~U
test for the cliff-detection check matches the independent-samples
structure of the data. Holm correction is applied per hypothesis
family to control the family-wise error rate.

\paragraph{Reproducibility.}
Every experiment writes a \texttt{manifest.yaml} that pins the
configuration hash, the git revision, the Python version, and the
platform string. Every CSV is reproducible from a single command. The
pricing constants live in one Python module and are updated in one
place.
