\thispagestyle{empty}
\header{\headerforeword}

This thesis was carried out at the Future Computing Group, CSE Research Unit,
Faculty of Information Technology and Electrical Engineering, University of
Oulu, in collaboration with TalentAdore Ltd. The work was supervised
academically by Lauri Lov\'en, with industrial supervision from Asim Nadeem
and Oskari Valkama at TalentAdore.

I owe my warmest thanks to Lauri for the latitude to scope a project around
an unfamiliar empirical question --- the way coordination under compression
behaves at institutional scale --- and for the discipline he brought to
keeping the scope tight. I am grateful to Asim Nadeem and Oskari Valkama for
sharing TalentAdore's production cost structure, which anchored the
cost-per-workflow arm of the evaluation in a real industrial setting. I
thank Mohammad Abaeiani, Faisal Khan, and Vu Truong for their willingness
to coordinate around the demands of this thesis.

The thesis was prepared on a single Apple M4 Pro 48~GB workstation
with an RTX~5090 32~GB GPU host on the Tailscale mesh for the
compression precomputation and the model-scaling and frontier-API
sweeps. The compute envelope, the reproducibility package, and the
open-source reference implementation are described in
Appendix~\charef{appendix}, Section~D.

\paragraph*{Use of generative-AI tools.}
This thesis was prepared with the assistance of generative-AI
tools. Specifically, Anthropic's Claude (accessed via the
Claude Code command-line interface) was used to (a) draft and
revise prose under the author's continuous supervision; (b)
assist with code review, refactoring, and debugging of the
experiment-orchestration and analysis scripts; and (c) cross-check
verdict-table numbers against the on-disk results CSVs during the
audit-reconciliation period. Every scientific claim, every
experimental design choice, every results-interpretation paragraph,
and the final manuscript text are the author's responsibility.
Recorded design decisions reached with AI-assisted brainstorming
are documented as architecture decision records (ADRs) in
\texttt{docs/adr/} of the repository and are cited in this manuscript
wherever they shape a load-bearing claim.

\signature
