This chapter presents the artefacts the empirical evaluation rests on:
the reference memory bus, the compressor framework, the multi-fragment
\emph{C1} coordination benchmark, the coordination-success and
critical-token-recall metrics that the cliff analysis turns on, the
precomputed compression cache that decouples compression from
evaluation, and the single-command reproducibility envelope. The
intent is to give a reader enough detail to reproduce the system from
the open-source repository without consulting the code, and to make
the design choices explicit so that the experimental results in
Chapter~\charef{experiments} can be read against the constraints
those choices imposed.

A scope reminder, stated once explicitly so that every claim in this
chapter and the next is bounded by it: the \emph{multi-fragment LLM
workflows} that this thesis evaluates are not multi-agent simulations.
The planner is a deterministic regex-based information-extraction
solver for the cliff sweep (Hypotheses~H1 and H2) and a single LLM
call with all (compressed) fragments visible for the model-scaling
sweep (Corollary~1, frontier validation, real-data transfer). The
memory bus is \emph{designed for} a future multi-agent integration
with an AutoGen back-end available in the source tree, but its
multi-agent operation is outside the empirical scope of this thesis.
This boundary is documented in CONTEXT.md and recorded as
ADR-009 in the project repository.

\section{The Memory-Bus Reference Implementation}
\label{sec:architecture}

\subsection{Three-layer architecture}

The reference implementation organises the memory bus into three
layers that match the access pattern of a fragment-passing workflow:

\begin{enumerate}
\setlength\itemsep{2pt}
\item An \textbf{access layer}, exposing \texttt{read},
\texttt{write}, \texttt{subscribe}, and \texttt{audit} endpoints via
FastAPI and enforcing per-request access-control checks through a
policy middleware.
\item A \textbf{compression layer}, providing a pluggable
\texttt{Compressor} protocol behind which six concrete variants live:
an \emph{identity} no-compression control, the
\emph{LLMLingua-2}~\cite{pan2024llmlingua2} token classifier, an
\emph{instruction-aware filter} based on TF--IDF pruning plus a
cross-encoder re-ranker, a \emph{Phi-3-Mini extractive} span selector
implemented over a local Ollama endpoint, a \emph{truncation}
prefix-keep baseline, and \emph{CAAC} --- a cliff-aware adaptive
wrapper that backs off compression when per-fragment recall would
violate the compounding-error model's safety threshold
(Section~\ref{sec:compressors_caac}, full discussion in
Chapter~\charef{summary}).
\item A \textbf{storage layer}, providing three protocols ---
\texttt{AuditLog}, \texttt{Scratchpad}, and \texttt{VectorStore} ---
implemented for the evaluation by SQLite in WAL mode with an
append-only audit table, an in-memory time-to-live dictionary, and
FAISS-CPU with an HNSW index.
\end{enumerate}

Figure~\ref{fig:architecture} summarises the three layers. Each
component dependency in the source tree is one-directional: the
compression layer does not import from the access layer, and the
storage layer does not import from either. This layering means the
storage backends can be replaced without touching the compression or
access layers.

\begin{figure}[h]
\centering
\begin{tikzpicture}[
    layer/.style={draw, rounded corners=2pt, minimum width=12cm,
                  minimum height=1.6cm, align=center, font=\small},
    cmp/.style={draw, rounded corners=1pt, minimum width=1.9cm,
                minimum height=0.6cm, font=\footnotesize},
    arrow/.style={-{Latex[length=2mm]}, thick},
    label/.style={font=\footnotesize\itshape}
]
% Access layer
\node[layer, fill=black!4] (access) at (0,4)
  {\textbf{Access layer (FastAPI)} \\[1pt]
   \footnotesize POST /v1/write \quad GET /v1/read \quad POST /v1/subscribe
   \quad GET /v1/audit \\
   \footnotesize PolicyMiddleware \quad StructLogMiddleware \quad OtelMiddleware};

% Compression layer
\node[layer, fill=black!4, minimum height=2.0cm] (compress) at (0,1.8)
  {\textbf{Compression layer} \\[2pt]
   \texttt{Compressor} protocol \\[2pt]};
\node[cmp] (id)     at (-5.0, 1.5) {identity};
\node[cmp] (lingua) at (-2.9, 1.5) {LLMLingua-2};
\node[cmp] (filter) at (-0.8, 1.5) {filter};
\node[cmp] (phi)    at ( 1.3, 1.5) {Phi-3 ext.};
\node[cmp] (trunc)  at ( 3.4, 1.5) {truncation};
\node[cmp] (caac)   at ( 5.5, 1.5) {CAAC (wrap)};

% Storage layer
\node[layer, fill=black!4, minimum height=2.0cm] (storage) at (0,-1.0)
  {\textbf{Storage layer} \\[2pt]};
\node[cmp, minimum width=3cm] (audit) at (-3.7, -1.3) {SQLite AuditLog};
\node[cmp, minimum width=3cm] (scr)   at ( 0.0, -1.3) {InMemory Scratchpad};
\node[cmp, minimum width=3cm] (vs)    at ( 3.7, -1.3) {FAISS VectorStore};

% Arrows between layers
\draw[arrow] (access) -- (compress);
\draw[arrow] (compress) -- (storage);

% Side annotations
\node[label] at (7.6,  4.0) {ACL-checked};
\node[label] at (7.6,  1.8) {pluggable};
\node[label] at (7.6, -1.0) {append-only};
\end{tikzpicture}
\caption{Three-layer architecture of the memory-bus reference
implementation. Each layer depends only on the layer below it, and
each storage component is hidden behind a \texttt{Protocol} so that
the storage backends can be replaced without touching the access or
compression layers. CAAC is drawn inside the compression layer for
convenience but is a wrapper: it composes any of the other
compressors with a recall-side back-off rule
(Section~\ref{sec:compressors_caac}).}
\label{fig:architecture}
\end{figure}

The three-layer structure is a direct extension of
MemIndex~\cite{saleh2025memindex}, the FCG group's baseline architecture
for distributed agent memory. The two material differences are that
compression is promoted to a first-class layer rather than treated as
a downstream optimisation, and that per-slot tags are part of the
data model rather than out-of-band metadata.

\subsection{Data flow for a write}

A single write request flows through the bus in the following order.
The client sends \texttt{POST /v1/write} with a JSON body containing
the fragment text, its tag vector, and an optional task hint. The
policy middleware parses the requester principal from the
\texttt{X-M6-Principal} header and writes it to
\texttt{request.state.principal} as a Starlette \texttt{State()}
attribute. The service receives the request, checks that the
principal's access-control mask is a superset of the fragment tag's
mask and that the principal's classification is at least the
fragment's classification, calls the active compressor's
\texttt{compress(fragment, target\_ratio)} method to produce a
\texttt{CompressedSlot}, places that slot in the in-memory scratchpad
keyed on the slot identifier, computes an embedding for the slot if
the compressor exposes one and adds it to the FAISS index, and
finally appends a row to the audit log whose
\texttt{event\_type} is \texttt{WRITE}, \texttt{result} is
\texttt{OK}, \texttt{prev\_hash} is the previous row's chain hash,
and \texttt{chain\_hash} is $\textsc{SHA-256}(\texttt{prev\_hash}
\mathbin\Vert \texttt{payload\_hash})$. The response carries the slot
identifier, the chain hash hex-encoded, and the audit row
identifier.

If the policy check fails, the bus appends a \texttt{DENY} row with
the synthesised slot identifier \texttt{deny-<uuid8>}, with a
$60$-second per-\textit{(subject, fragment-id)} deduplication so
that an adversarial client hammering denied writes cannot inflate
the audit log.

\subsection{Data flow for a read}

A read request flows symmetrically. The client sends \texttt{GET
/v1/read/\{slot\_id\}}, the policy middleware attaches the principal,
the service looks up the slot in the scratchpad, checks the
principal--tag relationship, and either returns the slot together
with the audit row identifier or raises a policy-denied or
slot-not-found error. The slot-not-found path is itself audited with
a 60-second per-\textit{(subject, slot-id)} deduplication: the first
read miss for a given subject and slot is appended to the audit log
as a \texttt{READ}/\texttt{ERROR} row, and subsequent misses within
the window short-circuit silently so that an adversarial reader
cannot inflate the audit log either. Appendix~\charef{appendix}
contains a verbatim \texttt{curl} trace exercising the write, read,
and audit endpoints end-to-end against the reference service.

\subsection{Tags, classifications, and the audit log}

Every fragment and every compressed slot carries a tag vector
recording its provenance and access-control state. The tag vector has
four fields: a \texttt{uint64} access-control mask, a five-tier
classification level (\textsc{public} $<$ \textsc{internal} $<$
\textsc{confidential} $<$ \textsc{restricted} $<$ \textsc{secret})
drawn from the NIST AI Risk Management
Framework~\cite{nistairmf}, a tuple of source identifiers recording
provenance, and a tuple of parent-slot identifiers recording which
previously-compressed slots this slot inherits from. When slots are
merged, the union's access-control mask is the bitwise OR of the
parents' masks and the union's classification is the maximum; the
policy predicate is symmetric for reads and writes.

The audit log is an append-only SQLite table whose columns are
listed in Table~\ref{tab:audit_columns}. An \texttt{INSTEAD OF
UPDATE} and an \texttt{INSTEAD OF DELETE} trigger refuse any mutation
of an existing row, and a unit test drops the trigger, edits a
\texttt{payload\_hash} at the byte level, and confirms that the
\texttt{verify()} chain-walker reports failure.

\begin{table}[h]
\centering
\caption{Schema of the SQLite \texttt{audit\_log} table. Triggers
prevent UPDATE and DELETE on this table at the database level.}
\label{tab:audit_columns}
\small
\begin{tabular}{p{2.6cm}p{3.1cm}p{8cm}}
\hline
Column & Type & Notes \\
\hline
\texttt{rowid} & INTEGER PK & monotonic, auto-increment \\
\texttt{slot\_id} & TEXT NOT NULL & matches the slot identifier \\
\texttt{event\_type} & TEXT CHECK & one of WRITE / READ / SUBSCRIBE / DENY / COMPRESS / EVICT \\
\texttt{requester\_acl} & INTEGER & 64-bit ACL mask, stored signed \\
\texttt{requester\_class} & INTEGER & classification level $0$--$4$ \\
\texttt{result} & TEXT CHECK & OK / DENIED / ERROR \\
\texttt{prev\_hash} & BLOB(32) & SHA-256 of the previous row's chain\_hash \\
\texttt{payload\_hash} & BLOB(32) & SHA-256 of the event's payload bytes \\
\texttt{chain\_hash} & BLOB(32) & SHA-256(prev\_hash $\Vert$ payload\_hash) \\
\texttt{created\_at} & TEXT NOT NULL & ISO-8601 UTC timestamp \\
\hline
\end{tabular}
\end{table}

A second SQLite table records every paid model call: provider,
model, input tokens, output tokens, EUR cost, and wallclock. The
cost ledger shares the audit-log database for transactional
consistency but is queried separately. Pricing constants are drawn
from the financial-analysis document~\cite{fcgfinancial2026}: the
frontier-cloud reference is approximately EUR~$2.76$ per million
input tokens and EUR~$13.80$ per million output tokens, and the
on-premises amortised marginal cost is EUR~$0.05$ per million
tokens. The ledger feeds the EUR-per-workflow cost model that
parameterises the RAG pipeline catalogue
(Section~\ref{sec:rag_pipelines}).

\section{Compressor Framework}
\label{sec:compressors}

Every compressor variant conforms to a single Python \texttt{Protocol}
with four methods --- \texttt{compress(fragment, target\_ratio)}
returning a \texttt{CompressedSlot}; \texttt{decompress(slot)}
returning a best-effort text reconstruction; \texttt{embed(slot)}
returning an optional embedding for vector-store indexing; and
\texttt{model\_card()} returning a structured card containing the
compressor identifier, family, base model, default target ratio, and
provenance hashes. The thesis ships six concrete implementations.
The identity compressor is the no-compression control condition
required by every experiment as a mitigation against runtime-bug
confounds.

The remaining five compressors fall into four families: a
token-level hard-prompt filter (LLMLingua-2); an instruction-aware
heuristic filter; an extractive small-LLM span selector
(Phi-3-Mini extractive); a trivial prefix-truncation baseline; and a
cliff-aware adaptive wrapper (CAAC). \emph{All five are
training-free}, which is a deliberate design choice: the thesis
isolates the compression mechanism from any training-data effect
and lets the cross-compressor comparison turn on the algorithm
rather than on training-budget asymmetry.

\subsection{LLMLingua-2 (token-level classifier)}

The LLMLingua-2 wrapper is a thin adapter around the
\texttt{llmlingua} package~\cite{pan2024llmlingua2}. Construction
takes a target compression ratio; the package is asked to retain
$1/r$ of the tokens, scored by a small XLM-RoBERTa classifier
distilled from a more capable teacher. The force-tokens list
(sentence boundary marks) is validated against the wrapped
tokenizer's vocabulary at initialisation and unknown tokens are
dropped with an explicit log line. The wrapped XLM-RoBERTa model
is supported by PyTorch on both CPU and Apple's Metal Performance
Shaders backend, so the compressor runs natively on Apple Silicon
without modification.

The empirical token-recall curve $q(r)$ produced by LLMLingua-2
under critical-token-recall measurement (Section~\ref{sec:ctr})
is smooth and monotonic across the sweep ratios used in
Chapter~\charef{experiments}, which is the property the
compounding-error model presumes.

\subsection{Instruction-aware filter}

The instruction-aware filter is a pure-Python heuristic baseline.
It operates in two stages. The first is a sentence-level filter
that ranks sentences by their relevance to the task hint using a
cross-encoder reranker (\texttt{BAAI/bge-reranker-base}) when
available and a lexical-overlap fallback when not. The second is a
token-level trim that drops English stop-words and short tokens
($\le 2$ characters) until the target compression ratio is reached.
The stop-word list is encoded explicitly so that the trim is
deterministic given the task hint, the fragment, and the target
ratio --- a subtle bug found during the development of this thesis
showed that dropping stop-words by Python set iteration order
introduced run-to-run variance, which is why the list is explicit.

The filter's reranker preserves task-keyword tokens that simpler
token-level methods drop, which is why its $q(r)$ curve on the
multi-step retrieval family (Section~\ref{sec:c1}, family-c) decays
gracefully rather than collapsing: chain-reference tokens like
``entry'' and ``FINAL'' survive aggressive compression.

\subsection{Phi-3-Mini extractive span selector}

The Phi-3-Mini extractive compressor is the only thesis compressor
that uses an LLM at inference time. It runs the Phi-3-Mini-3.8B
instruction-tuned model~\cite{phi3} via a local Ollama
endpoint~\cite{ollama} with a structured prompt that asks for
verbatim contiguous spans from the source. The post-hoc verifier
\texttt{Phi3ExtractiveCompressor.\_verify\_extractive} checks the
output: every token in the output must appear in the source. Two
loosenings of the strict verifier were necessary in practice. First,
a $15\%$ novel-token tolerance: small language models frequently
insert function words (``the'', ``is'', ``and'') even when
explicitly asked not to. Second, a post-hoc
\texttt{\_strip\_novel\_tokens} pass that removes any token not in
the source after the verifier passes; this guarantees zero novel
tokens in the final output even if the model produced some during
generation. Outputs that fail even after stripping fall back to
LLMLingua-2 at the same target ratio.

A practically important property of Phi-3-Mini extractive is its
\emph{compression ceiling}. Span-level selection plus the stripping
pass plus the LLMLingua-2 fallback combine to bound the achievable
compression ratio at approximately $2.5\times$, regardless of the
requested target. This is documented as a limitation in
Chapter~\charef{summary} and is the reason all evaluation reports
\emph{achieved} compression ratio (the ratio actually delivered)
alongside the requested target ratio.

\subsection{Truncation (prefix-keep baseline)}

The truncation compressor keeps the first $1/r$ fraction of tokens
by whitespace split. It is deterministic by construction and
achieves the requested ratio exactly. Its purpose is the
lower-bound argument: every more sophisticated compressor must
beat truncation on the coordination metric to justify its cost.

Truncation has a peculiar property: its single-agent
question-answering F1 is competitive with the more sophisticated
compressors at low to moderate compression ratios because the
prefix tokens are naturally representative. Its coordination
success collapses earlier than the others, because the tokens
removed at the tail include the task-critical content that the
planner needs to combine. This dissociation is part of the H1
finding: a token-overlap quality metric over-reports the utility
of even the most naive compressor.

\subsection{Cliff-Aware Adaptive Compression (CAAC)}
\label{sec:compressors_caac}

CAAC is a wrapper, not a fifth compressor family. Given an inner
compressor (LLMLingua-2 in the headline experiments; any of the
others in the ablation) and a per-family recall threshold
$\theta_q$, CAAC runs the inner compressor at the requested target
ratio, measures the resulting critical-token-recall, and if recall
falls below $\theta_q^{1/N}$ binary-searches downward for the
largest ratio that keeps recall above the threshold. A
\texttt{min\_ratio} floor of $1.5\times$ prevents CAAC from
abdicating to no-compression on hard fragments. The full
algorithmic and empirical discussion lives in
Chapter~\charef{summary} together with the constructive framing
that CAAC is the operational realisation of the compounding-error
bound. Here it suffices to note that CAAC consumes the same
\texttt{Compressor} protocol as the other variants, which is what
makes its drop-in evaluation in Chapter~\charef{experiments}
straightforward.

\section{The C1 Coordination Benchmark}
\label{sec:c1}

\subsection{Why a synthetic benchmark}

The empirical centrepiece of this thesis --- the
\emph{coordination cliff}~$\tau^{*}$ --- is a position on a curve.
Detecting and characterising a cliff requires sweeping compression
ratios densely from $1\times$ to $16\times$, holding everything else
constant, and reading off where coordination success crosses a
threshold. Real-world benchmarks (HotpotQA, MultiHopRAG) confound
the cliff with task difficulty, retrieval distribution, dataset
bias, and per-instance variance. The thesis takes the position that
the cliff is best characterised on a synthetic generator first,
where information density can be placed by construction, and then
externally validated on real benchmarks. The synthetic-first
posture is responsible for the clean Chapter~\charef{experiments}
results on H1, H2, and Corollary~1; the real-benchmark validation
of Corollary~2 confirms that the structure transfers.

The C1 generator produces $150$ instances across three workload
families and is reproducible from a single seed. The configuration
hash and the resolved configuration are recorded in the manifest
alongside the generated workloads so that any output CSV can be
traced back to the exact generator inputs that produced it.

\subsection{Three workload families}
\label{sec:c1_families}

\begin{description}\setlength\itemsep{2pt}

\item[Family-a --- cross-document fact aggregation.] Each instance
provides eight source documents, one per system from the
Vignette~3.7 institutional inventory (Publication~DB, Contract~DB,
Moodle, Patio, Peppi, CRM, Tatu~SAP,
SAP~Travel~\cite{fcgusecase2026}). Each document carries one
recorded-hours and one approved-budget number drawn from a
seed-fixed distribution. The planner is asked to aggregate the two
quantities across the eight documents. Ground truth is the
arithmetic sum, deterministic from the seed; the scorer is a
regex-based extraction pipeline that matches \emph{hours:\,X} and
\emph{budget: EUR\,Y} patterns. Family-a is the densest of the
three: every multi-digit number is task-critical, and
$\theta_\text{info}\approx 0.97$ (Section~\ref{sec:theta_info_def}).
The family-a cliff is sharp; it is the family on which the
compounding-error model is most directly testable.

\item[Family-b --- constraint-satisfaction planning.] Each instance
specifies $N$ sub-tasks with per-task loads and $K$ workers with
per-worker capacities. The planner must produce an assignment of
sub-tasks to workers that respects per-worker capacity and assigns
every sub-task. The generator constructs a feasible solution by a
capacity-respecting greedy algorithm that bumps capacities only when
strictly necessary, guaranteeing that every workload has at least
one feasible assignment. The scorer is a \emph{feasibility checker}
rather than an exact-match: any assignment that satisfies the
constraints scores~$1$, so the planner is rewarded for finding
\emph{any} solution rather than memorising one. Family-b exposes a
property of small LLM planners that is independent of compression:
constraint tracking is hard for $\le 8$B-parameter models even
without compression, so the family-b baseline success $p_0$ is low
for small planners and the cliff is not detectable in that regime ---
a \emph{floor effect} that Chapter~\charef{experiments} treats
explicitly.

\item[Family-c --- multi-step retrieval.] Each instance presents a
linear chain of fragments where each fragment carries either a
pointer to the next (\emph{entry~X}) or, at the leaf,
the answer (\emph{FINAL-XXXX}). Chain lengths range from $2$ to $4$;
each fragment is padded with $4$ to $8$ distractor sentences so
that the retrieval step is non-trivial. The scorer reads the
planner's output and matches against the leaf answer. Family-c is
the most distributed of the three: many tokens are distractors,
information density $\theta_\text{info}\approx 0.59$, and the cliff
is gradual --- it is the family on which the
instruction-aware filter's reranker, which preserves
chain-reference keywords, can avoid a detectable cliff entirely.
\end{description}

Each family contributes $50$ instances. The three families together
span a deliberate range of information densities so that the cliff
mechanism (a recall threshold $\theta_q$) and the cliff-position
shift mechanism (information density $\theta_\text{info}$) can be
separated; this separation is what Chapter~\charef{experiments}
formalises as Corollary~2.

\subsection{Tag distributions for the privacy axis}

The C1 generator supports three synthetic tag distributions ---
\emph{uniform}, \emph{skewed}, and \emph{hierarchical} --- used by
H4 (inference disclosure) to probe the governance-stringency
dimension. The hierarchical distribution sets higher classification
levels to imply strict supersets of the bits at lower levels, which
matches the real-world structure of NIST-RMF tag
hierarchies~\cite{nistairmf} and lets the H4 analysis disentangle
classification level from access-control mask.

\subsection{Coordination success and supporting metrics}

The coordination scorer is a pure function of the workload and the
planner's output; it does not call any LLM. It returns one primary
metric --- a per-instance binary \emph{coordination success} --- and
four supporting metrics: the F1 over extracted answer tokens versus
ground truth, the achieved compression ratio
($|\text{source}|/|\text{compressed}|$), generic token-recall (the
fraction of source tokens preserved in the compressed text), and
\emph{critical-token-recall} (CTR; Section~\ref{sec:ctr}).
Aggregation across workloads $\times$ seeds is by arithmetic mean;
$95\%$ confidence intervals are computed by workload-level
bootstrap, never by per-row bootstrap which double-counts the seed
dimension.

The reason the scoring pipeline never calls an LLM is the same
reason H1 and H2 use a deterministic regex parser as the planner:
isolating the compression-quality signal from LLM run-to-run
variance. The trade-off is that the cliff measured here is an upper
bound on what an LLM-based scorer would measure; the trade is in
favour of clean attribution rather than ecological validity, and
Chapter~\charef{summary} discusses the limitation.

\subsection{The critical-token-recall metric}
\label{sec:ctr}

A standard token-recall measurement
$q_\text{token}(r) = |T_\text{compressed} \cap T_\text{source}| /
|T_\text{source}|$ counts every preserved token equally. This
turned out, during the development of this thesis, to be a poor
proxy for task-relevant information preservation: the Phi-3-Mini
extractive compressor at low ratios preserves common function
words like ``the'' and ``and'' but drops some critical numeric
tokens. Its token-recall is high; its coordination success is low.

The critical-token-recall (CTR) metric is the family-specific
restriction:
\[
  q_\text{CTR}(r) = \frac{|T_\text{compressed}^{\,\text{crit}} \cap
                          T_\text{source}^{\,\text{crit}}|}
                         {|T_\text{source}^{\,\text{crit}}|},
\]
where $T^\text{crit}$ is the set of \emph{task-critical} tokens for
the family:
\begin{itemize}\setlength\itemsep{1pt}
\item Family-a: multi-digit numeric tokens (at least two digits, to
exclude single-digit noise);
\item Family-b: all numeric tokens (load and capacity values);
\item Family-c: chain-reference tokens (\emph{entry-X} patterns) and
the literal \emph{FINAL} marker.
\end{itemize}

CTR is what the compounding-error model uses as the per-round
retention rate $q(r)$; CAAC uses CTR as its back-off signal; and
the predicted-versus-empirical $\tau^{*}$ figure in
Chapter~\charef{experiments} uses CTR to derive $\theta_q$. Generic
token-recall is reported for backwards compatibility with prior
analyses but is not used in the verdict pipeline.

\section{Compression Cache}
\label{sec:cache}

Compression is the slowest step in the evaluation. LLMLingua-2 at a
single ratio over $150$ workloads takes minutes; Phi-3-Mini
extractive over the same range takes hours because each fragment is
a $\sim 11$~second Ollama call including verification and possible
retry. The cliff sweep requires every (compressor, ratio, workload,
task-hint) cell --- approximately $30{,}000$ cells in the canonical
H1/H2 protocol --- and a naive nested-loop implementation that
recompresses on every evaluation pass would dominate the wallclock.

The thesis ships a precomputed compression cache,
\texttt{CompressionCache} and \texttt{CachedCompressor} in
\texttt{src/m6/compressors/cache.py}, with cache keys
$(\text{compressor}, r, \text{fragment\_id}, \text{hash}(\text{task\_hint}))$.
The cache is a JSON store for portability; the task-hint hash is
the first twelve characters of an MD5 so that the keys are short
enough to remain readable. The cache is populated once by the
\texttt{precompute\_cache.py} script on the GPU server and all
subsequent runs consume the JSON. This decoupling is what makes
the evaluation pipeline runnable end-to-end on a laptop without
the GPU: H1, H2, the frontier API sweep, and the CAAC ablation
all consume the cache rather than the live compressors.

The compression cache is also a methodological device. It
guarantees that every evaluation in Chapter~\charef{experiments}
sees the exact same compressed text for a given (compressor, ratio,
workload) cell, so that any difference between runs is attributable
to the evaluation protocol rather than to compressor stochasticity.
The cache hit rate over the canonical sweep is $100\%$ by
construction.

\section{Inference Backends}
\label{sec:inference}

The unified \texttt{InferenceBackend} protocol exposes a single
\texttt{complete(prompt, max\_tokens, temperature, stop)} method
together with an optional \texttt{embed(text)} method. Three concrete
backends are used in the evaluation. The first is a local Ollama
endpoint~\cite{ollama} that hosts Qwen-2.5-Instruct at the three
local sizes (\textsc{1.5B}, \textsc{3.8B}, \textsc{8B}) used in
the model-scaling sweep, Phi-3-Mini-3.8B for the extractive
compressor, and Llama-3.1-8B-Instruct as the local protected-fact
reader. The second is the OpenAI-compatible Featherless API used
for the frontier validation (Qwen-2.5-72B-Instruct, DeepSeek V4
Pro). The third is the OpenAI API for the GPT-class frontier
arm (excluded from the calibrated regime per
Chapter~\charef{summary}, retained on disk as a noncanonical
diagnostic). All API calls are routed through the cost ledger so
that the EUR-per-workflow figures in
Chapter~\charef{experiments} are auditable.

\section{Scope of Evaluation: the Multi-Fragment Proxy}
\label{sec:scope}

The empirical protocol uses two planners. H1 and H2 use a
deterministic regex-based information-extraction solver that parses
the compressed fragments for the task-critical patterns of
Section~\ref{sec:c1_families}; its purpose is to isolate the
compression-quality variance from LLM run-to-run variance.
Corollary~1 (the model-scaling sweep), the frontier validation, and
the real-data transfer arms use a single LLM call with all
(compressed) fragments visible in a flat prompt; their purpose is
to demonstrate that the cliff structure measured by the
deterministic solver appears identically when the planner is a
non-trivial language model.

An AutoGen v0.4 multi-round agent backend
exists~\cite{wu2023autogen} in \texttt{src/m6/orchestrator/} and
integrates with the memory bus described in
Section~\ref{sec:architecture}. It is not used in the empirical
evaluation. The decision is documented as ADR-009 in the
repository: the run-to-run variance introduced by multi-round
agent negotiation dominates the compression signal at the C1
ratios this thesis sweeps, and the value of the AutoGen runner is
to demonstrate that the memory-bus design is multi-agent-ready,
not to be the planner whose cliff is measured. The boundary is
that the memory bus is \emph{designed for} multi-agent
integration; the experiments \emph{evaluate} on a multi-fragment
proxy.

Coordination success, as defined in
Section~\ref{sec:c1}, refers to the structural task property that
the planner must combine information drawn from multiple
fragments. It does not refer to the multi-round communication
quality between agents; that property is what the AutoGen backend
would enable measuring in future work, and is named in
Chapter~\charef{summary} as part of the limitations and the
future-work roadmap.

\section{Compute Envelope and Reproducibility}
\label{sec:envelope}

The empirical work runs on two machines. The first is an Apple~M4
Pro 48~GB workstation, which hosts the local Ollama planners for
the cliff sweep development and the deterministic-solver pipeline,
and which is sufficient for every figure and verdict in
Chapters~\charef{experiments} and~\charef{summary} when the
compression cache is in place. The second is an RTX~5090 32~GB
workstation (Tailscale-accessible WSL2 host) used for the
compression precomputation, the model-scaling sweep at \textsc{8B},
the frontier API sweep, and the HotpotQA / MultiHopRAG transfer
arm. Total wallclock for the canonical evaluation pipeline (cache
precompute on GPU + cliff sweep + scaling + RAG + disclosure +
real-data transfer) is approximately $30$ hours of GPU time and
$\sim 12$ hours of laptop time end-to-end.

The reproducibility package is the complete repository: a
\texttt{docker-compose.yml} that brings the memory-bus reference
service up locally, a GitHub release tag for the manuscript and
code, model and data cards under \texttt{docs/}, and a
\texttt{README.md} that exposes one-command reproduction for every
chapter headline figure. The filesystem layout under
\texttt{results/} is fixed: one CSV per hypothesis run plus a
\texttt{manifest.yaml} that records the resolved configuration,
the configuration hash, the git revision, the Python version, the
platform string, and the start time. Appendix~\charef{appendix}
describes the package contents in detail and lists every command
needed to reproduce the headline figures.
