\section{Motivation: Every Token Has a Cost}
\label{sec:motivation}

Large language models pay for every token they read. The cost is
measurable at three layers: the energy and water needed to power a
prefill and a decoding pass; the latency the user pays to wait for
that pass to complete; and the dollar amount the operator pays per
million tokens through an API or amortises through on-premises
hardware. Peer-reviewed measurements of inference-side energy are
recent --- Luccioni \emph{et~al.}'s 2024 \emph{Power Hungry
Processing} study reports per-inference Watt-hour numbers for a
broad set of open models, and finds that the wall-power cost of a
single text-generation inference call on a modestly-sized model is
within an order of magnitude of the wall-power cost of an
internet search~\cite{luccioni2024powerhungry}. When the workload
is a multi-step agentic system that issues thousands of internal
inference calls to answer a single user request, those costs
compound.

A growing fraction of the tokens a deployed LLM reads do not
change the answer. They are conversational filler (``Hello'',
``Thanks''), repeated system prompts that scaffold every call,
restated history that re-anchors a long conversation, boilerplate
disclaimers, and structural framing that an attentive reader could
elide without loss. The industry rough estimate, widely reported
in 2025, was that OpenAI's compute bill for processing user
politeness alone amounted to ``tens of millions of dollars''
annually~\cite{altman2025pleasethankyou}. The number is reported
as industry observation, not as peer-reviewed measurement, but the
direction is consistent with the Luccioni
result~\cite{luccioni2024powerhungry}: tokens that do not change
the answer are converted directly into energy, latency, and
operating expense.

Context compression is the natural lever. Per-token compute and
per-token cost scale roughly linearly in sequence length once
the prefill is past the GPU memory-bound regime; halving the input
context halves the cost. The single-agent prompt-compression
literature has matured rapidly over the past three years
\cite{jiang2023llmlingua, jiang2024longllmlingua, pan2024llmlingua2,
mu2023gist, chevalier2023autocompressor, ge2024icae}. What has not
yet been measured, and what this thesis sets out to measure, is
whether the compression that preserves the standard single-agent
question-answering metric --- token-overlap F1 against a ground-
truth answer --- also preserves the harder structural property
that a planner needs: combining information distributed across
multiple fragments into a correct answer.

\section{The Multi-Fragment Workflow}
\label{sec:multi_fragment}

The setting this thesis studies is the \emph{multi-fragment LLM
workflow}: a task in which the answer cannot be read out of any
single fragment in isolation and requires combining information
across two or more fragments, each of which may be compressed
independently before the planner sees it. Cross-document fact
aggregation (sum eight numbers reported by eight different
institutional systems), constraint-satisfaction planning
(assign $N$ sub-tasks to $K$ capacity-bounded workers given
specifications spread across fragments), and multi-step retrieval
(chain references through a sequence of documents until a leaf
answer is reached) are three representative examples; the C1
benchmark of Chapter~\charef{implementation} constructs $50$
instances of each. The setting is not a corner case. The FCG group
at the University of Oulu's flagship use case ---
\emph{Vignette~3.7 -- Period-end project reporting}~\cite{fcgusecase2026}
--- gathers reporting data across eight university systems via
roughly eight specialised agents, achieves an estimated $80\%$
cloud-payload reduction, and reduces the per-report cost to
approximately EUR~$2.15$. TalentAdore, the industry partner of
this thesis, runs production workloads whose operating expenses
are dominated by token cost. Anthropic's own published report on
their multi-agent research system notes that token usage explains
approximately $80\%$ of the performance variance they
observe~\cite{anthropic2025multiagent}; the corresponding
context-engineering and context-editing reports describe an
$84\%$ token reduction on a 100-turn web-search
evaluation~\cite{anthropic2025contextediting,
anthropic2025contextengineering}. These are industry observations
on industry workflows; the master's-scale problem is the
controlled cross-compressor, cross-task, cross-architecture
measurement that turns the industry urgency into a technical
question.

The technical question this thesis takes up does not include the
multi-round agent-negotiation question that the
``multi-agent'' framing of the FCG and Anthropic systems would
imply. The empirical evaluation of this thesis uses either a
deterministic regex-based information-extraction solver or a
single LLM call with all (compressed) fragments visible as the
planner. An AutoGen v0.4 multi-round agent backend integrated
with the memory bus is shipped in the source tree
(\texttt{src/m6/orchestrator/}~\cite{wu2023autogen}) but is not used
in any reported result. The scope decision is documented as
ADR-009 in the repository. The motivation is that round-to-round
LLM variance dominates the compression signal at the C1
compression ratios that this thesis sweeps; cleanly attributing
coordination-quality drops to compression rather than to
multi-round agent variance requires isolating the compressor on
the critical path, which a single-LLM-call (or a deterministic
regex) planner does. The memory bus is \emph{designed for} a
multi-agent integration; the experimental scope is
multi-fragment task solvability. The chapter on the system design
(\ref{sec:scope} of Chapter~\charef{implementation}) restates
this scope decision explicitly; every results chapter is
calibrated against it.

\section{Problem Statement}
\label{sec:problem}

\emph{How does context compression affect multi-fragment
coordination quality across compressors, task structures, and
planner scales --- and when and how can a memory-bus service
exploit that understanding to compress safely, predictably, and
privately?}

The question subdivides into four operationally distinct sub-
questions, one per contribution.
First, a benchmark question: what does a coordination-quality
metric on a multi-fragment workflow look like, and how should it
differ from single-agent question-answering accuracy?
Second, a characterisation question: does compression introduce a
\emph{coordination cliff} --- a compression ratio beyond which
coordination success collapses sharply --- and what determines
its position?
Third, a deployment question: how should compression be combined
with retrieval in a retrieval-augmented-generation pipeline, and
what is the cost trade-off across pipeline architectures?
Fourth, a governance question: can compression be measured as a
privacy lever, and can a memory-bus service expose that lever as
a deployment-time enforcement mechanism?

The thesis answers all four with four artefacts, each delivered
end-to-end and reproducible from the open-source repository.

\section{Contributions}
\label{sec:contributions}

\paragraph{C1 --- A reproducible multi-fragment coordination
benchmark.}
\emph{The C1 benchmark} ships $150$ instances across three
workload families (cross-document fact aggregation,
constraint-satisfaction planning, multi-step retrieval), with
synthetic provenance and access-control tag distributions, four
coordination-quality metrics (final task success, sub-task
assignment accuracy, critical-token-recall, achieved compression
ratio), and a single-command regeneration script from a fixed
seed. The benchmark is the substrate on which the cliff
characterisation, the model-scaling result, and the inference-
disclosure measurement all run; releasing it as part of the
thesis lets other groups extend the characterisation to new
compressors and new planner regimes.

\paragraph{C2 --- Empirical characterisation of the coordination
cliff and a compounding-error model that predicts it.}
\emph{The cliff exists, is sharp, and is invariant to planner
parameter count and architecture family within a defined
calibrated regime.} The empirical work covers four training-free
compressors --- LLMLingua-2~\cite{pan2024llmlingua2}, the Phi-3-
Mini extractive span selector, an instruction-aware filter, and a
truncation baseline --- at ten compression ratios across three
families and across three local planners drawn from
\textbf{three different architecture families}
(Qwen-2.5-1.5B-Instruct, Phi-3-Mini-3.8B-Instruct,
Llama-3.1-8B-Instruct; the original ``Qwen-2.5 1.5B/3.8B/8B''
notation conflated three architectures and is corrected here),
with a frontier validation arm on Qwen-2.5-72B and DeepSeek~V4~Pro
that carries the corollary's binary verdict across the strict
tolerance: Qwen-2.5-72B cliffs $\sim 7\%$ above the canonical
synthetic reference $\tau^{*}=2.5$ and inside its bootstrap CI;
DeepSeek~V4~Pro's bootstrap CI contains the synthetic reference.
(The local three-architecture sweep on family-c shows a $24\%$
tau spread, below the $50\%$ tolerance the validator originally
shipped with but above the strict $20\%$ tolerance --- necessary
but not sufficient; the load-bearing evidence is the
cross-architecture frontier arm. The local arm is itself a
cross-architecture invariance result across Qwen, Phi-3, and
Llama, not a within-family parameter-count sweep.) The
compounding-error model derives the cliff position from per-round
\textbf{critical-token-recall} and a per-family recall threshold
$\theta_q$ and recovers the empirical position within a useful
first-order tolerance. The same machinery supports
\textbf{Corollary~2 (information-density scaling)}: the cliff
\emph{shape} varies with a task's information density
$\theta_\text{info}$ (an AUC-based per-task quantity, distinct
from $\theta_q$), validated on HotpotQA and MultiHopRAG against
the C1 family-a synthetic reference. An out-of-regime diagnostic
on GPT-oss~120B identifies extended-reasoning planners as a
structurally distinct case that the model's threshold-success
assumption does not cover --- which is itself a contribution,
since prior compression work treats reasoning regime implicitly.

\paragraph{C3 --- A catalogue of three retrieval-augmented-
generation pipelines with a EUR-per-workflow cost model.}
Three pipeline architectures (compress-first, retrieve-first,
joint relevance-conditional routing) are implemented end-to-end on
FAISS-CPU and HNSW and evaluated under matched storage-bounded
and accuracy-bounded regimes. The original H3 hypothesis predicted
a sign-flip in the optimal pipeline between regimes; the empirical
work shows that compress-first is robustly preferred in both
regimes (by 3.2 pp F1 storage, 2.0 pp F1 accuracy), and the
joint relevance-conditional routing (P3) leads both
\textbf{by a substantial margin (42 pp F1 storage, 25 pp F1
accuracy)} at near-identical EUR-per-query cost. The compress-first preference \emph{reverses} a common
assumption of the LongLLMLingua~\cite{jiang2024longllmlingua}
line of work and is the substantive C3 finding, registered
honestly as a reframing of the original predicate.

\paragraph{C4 --- A memory-bus reference implementation and a
summary-level inference-disclosure metric.}
The memory bus is a FastAPI service with a tamper-evident SQLite
audit log, a policy middleware that enforces a five-tier
classification lattice over a $64$-bit access-control mask, an
in-memory scratchpad with TTL eviction, and a FAISS-CPU vector
store. The compressor abstraction is a Python protocol that all
five compressor variants satisfy. The summary-level
inference-disclosure metric quantifies how compression at
$4\times$ reduces the rate at which a held-out local Llama-3.1-8B
reader can recover protected facts from a compressed
\textsc{confidential} fragment. The metric ranks compressors by
disclosure rate at iso-ratio, and the memory bus's policy layer
operationalises the ranking as a deployment-time enforcement
mechanism; Section~\ref{sec:h4_construct} documents that the
ranking is monotonic in how aggressively each compressor destroys
source tokens (truncation at the top), which calibrates the
privacy interpretation against the destruction baseline.

The thesis also presents \textbf{CAAC} (Cliff-Aware Adaptive
Compression), a wrapper that operationalises the compounding-
error bound as a runtime back-off: given a per-family recall
threshold, CAAC binary-searches downward over compression ratios
until the per-fragment critical-token-recall sits on the safe
side of the cliff. CAAC is presented in
Chapter~\charef{summary} as a constructive demonstration of the
compounding-error model rather than as a fifth headline
contribution; the demonstration is that the cliff bound is not
only descriptive but operational.

\section{What Is Novel}

The closest published industry analogue to C2 is Anthropic's
report that token usage explains approximately $80\%$ of the
performance variance in their multi-agent research
workflow~\cite{anthropic2025multiagent}. That is an industry
observation on a single workflow run by a single team; the C2
contribution is the controlled cross-compressor, cross-family,
cross-architecture sweep with a quantitative model, an empirical
match-rate measurement, and a frontier-model validation. The
closest published academic analogue is the single-agent
question-answering evaluation of the LLMLingua line of
work~\cite{jiang2023llmlingua, jiang2024longllmlingua,
pan2024llmlingua2} and the long-context benchmarks
LongBench~\cite{bai2024longbench} and
RULER~\cite{hsieh2024ruler}; H1 shows that those evaluations
\emph{over-report} compressor utility for multi-fragment
deployment because the single-agent metric they measure does not
predict coordination success. The multi-fragment-specific
characterisation is the novelty.

The compounding-error model is novel in its application to
multi-fragment compression evaluation. The derivation is short
and the threshold-success assumption is a first-order
approximation, but the combination of a quantitative
position-prediction with a bootstrap-CI band on the prediction
and a per-cell empirical match-rate measurement is, to the
author's knowledge, not present in the prior compression
literature.

The summary-level inference-disclosure metric (C4) is distinct
from prior privacy-aware retrieval work
\cite{zhou2025privacyrag, bassit2025securerag}, which protects
the retrieval index from leaking; the metric this thesis
contributes measures leakage \emph{through the compressor
itself}, which is a separate axis. The memory-bus reference
implementation makes the metric auditable as a deployment-time
governance budget rather than a per-publication number.

\section{Thesis Outline}
\label{sec:outline}

The remaining chapters are organised as follows.

Chapter~\charef{relatedwork} surveys the prior work the four
contributions build on, organised into five strands: the
transformer architecture and the cost of context, the modern
training-free context-compression literature, multi-agent LLM
systems, retrieval-augmented generation, and privacy in agentic
memory. Each section closes by naming the gap that this thesis
fills relative to the prior work it surveys.

Chapter~\charef{implementation} presents the artefacts the
empirical evaluation runs on: the three-layer memory-bus
architecture, the compressor framework, the C1 benchmark
generator and scoring pipeline, the critical-token-recall metric,
the compression cache, and the multi-fragment scope of the
evaluation.

Chapter~\charef{experiments} presents the empirical work: H1
(question-answering accuracy decorrelates from coordination
success); H2 (a sharp coordination cliff exists, characterised
across $12$ compressor-family cells); the compounding-error
model that predicts the cliff position with a predicted-versus-
empirical match-rate band; Corollary~1 (the cliff position is
invariant to planner parameter count and architecture family
within a defined calibrated regime, validated on two frontier
models --- Qwen-2.5-72B and DeepSeek V4 Pro --- with GPT-oss 120B
reported as an out-of-regime diagnostic at the regime boundary);
H3 (the RAG pipeline catalogue with the compress-first dominance
result); H4 (the inference-disclosure measurement on the unbiased
benchmark); and Corollary~2 (the cliff \emph{shape} varies with
task information density across three benchmarks).

Chapter~\charef{summary} synthesises the findings, presents CAAC
as the constructive realisation of the compounding-error bound,
enumerates the limitations, discusses the practitioner and
field-level significance, compares the findings to industry
observations, and names the future-work directions in order of
expected impact.

All artefacts --- the manuscript source, the code, the
configuration files, the results CSVs, and the
\texttt{docker-compose.yml} that brings the memory-bus reference
service up locally --- are released under a permissive licence in
the open-source repository. Appendix~\charef{appendix} describes
the reproducibility package and the one-command reproduction
recipe for every headline figure.
