This chapter surveys the prior work the four contributions of this
thesis build on. It is organised into seven strands.
Section~\ref{sec:rw_transformer} introduces the transformer
architecture and the per-token compute and memory cost that
context-compression aims to reduce.
Section~\ref{sec:rw_scaling} sketches the
scaling-law trajectory and the inference-cost asymmetry that
followed.
Section~\ref{sec:rw_cost} surveys the published
energy and economic measurements of inference at scale, which
underpin the motivation chapter.
Section~\ref{sec:rw_compression} covers the modern training-free
context-compression literature.
Section~\ref{sec:rw_multiagent} covers multi-agent LLM systems
and agentic memory.
Section~\ref{sec:rw_rag} covers retrieval-augmented generation,
long-context benchmarks, and the evaluation suite that frames C3.
Section~\ref{sec:rw_privacy} covers privacy-aware retrieval and
the inference-disclosure literature.
Each section closes by naming the gap that this thesis fills
relative to the prior work it surveys; the consolidated gap
statement is Section~\ref{sec:rw_gap}.

\section{The Transformer Architecture and the Cost of Context}
\label{sec:rw_transformer}

The artefacts of this thesis are built around large language
models whose architectural foundation is the
transformer~\cite{vaswani2017attention}. The transformer's
defining mechanism is \emph{self-attention}: each token in a
sequence computes a weighted sum of representations of every
other token in the same sequence, with the weights determined by
the compatibility of learned query and key projections of the
respective tokens. For a sequence of length~$N$ and a hidden
size~$d$, the self-attention mechanism produces $N^2$
compatibility scores (a quadratic-in-$N$ memory and compute cost)
and a final $N \times d$ output. The transformer block
interleaves self-attention with a position-wise feed-forward
network whose cost is linear in $N$ but proportional to the
square of the hidden size $d$. Stacking $L$ such blocks gives
total prefill compute approximately $L \cdot (N^2 d + N d^2)$
floating-point operations per forward pass and a memory
footprint dominated by the key-value cache of size
$L \cdot N \cdot d_{\text{kv}}$ bytes per request, which grows
linearly in $N$ and is paid for every token through the
autoregressive decoding loop.

The decoder-only sub-family of the transformer architecture is
the one this thesis evaluates. The original
transformer~\cite{vaswani2017attention} was encoder--decoder; the
encoder-only line gave us BERT and its descendants; the decoder-
only line gave us GPT-2, GPT-3, GPT-4, and the open-source
families that this thesis's planners are drawn from (Qwen,
Llama, DeepSeek, Phi-3). The reasons decoder-only architectures
came to dominate large-scale deployment are three. First, the
training objective is uniform across all token positions
(next-token prediction), which scales cleanly with data and
parameters. Second, the autoregressive decoding loop allows the
key-value cache to be amortised across token positions after the
prefill, which makes each generated token cheap relative to the
context that was loaded. Third, the in-context-learning
behaviour that motivated agentic systems is a decoder-only
phenomenon: the model conditions its output on a long prefix
without further training. The practical implication for context
compression is that the cost a deployed decoder-only model pays
per query is roughly $2 \cdot P \cdot N$ floating-point
operations during prefill (where $P$ is the parameter count) and
a per-decoded-token cost that is dominated by the key-value cache
loaded from the prefill. Halving the prefill-length $N$ halves
both costs. This is the lever context compression operates on.

The scaling laws of large language models give one final piece of
the cost picture. Kaplan \emph{et~al.}~\cite{kaplan2020scalinglaws}
showed that the loss of a transformer trained on next-token
prediction follows an approximate power-law in parameters,
training tokens, and compute, with prescriptive implications for
how to allocate a fixed compute budget between model size and
training data. Hoffmann \emph{et~al.}~\cite{hoffmann2022chinchilla}
refined this with the \emph{Chinchilla} prescription that
parameters and training tokens should scale proportionally for
compute-optimal training. The training-time scaling laws gave the
field a recipe to spend training compute productively; what they
did not give is a corresponding recipe to spend
\emph{inference} compute productively. Inference cost is paid
per query for the deployment lifetime of the model, and at
production scale it dominates training cost over a small number
of months. Context compression is to inference cost what scaling
laws are to training cost: a structural lever that converts a
linear cost in some axis into a constant cost.

\emph{What this thesis adds.} The cost framing this section
provides is the motivation backdrop. What is missing in prior
work is a structural characterisation of how aggressive
compression interacts with the per-token cost reduction it
delivers when the downstream task requires combining information
across multiple compressed fragments rather than reading a
single answer out of a single fragment. The cliff measurement of
Chapter~\charef{experiments} fills that gap.

\section{The Scaling Era of LLMs}
\label{sec:rw_scaling}

The trajectory from GPT-2 (1.5B parameters, 2019) to GPT-3
(175B, 2020) to GPT-4 (undisclosed, 2023) to the frontier of
2025--2026 (Llama-3, Qwen-2.5, DeepSeek V3 and V4, Claude
Sonnet 4.x, GPT-oss) marks a four-order-of-magnitude growth in
deployed model size. Each step was accompanied by a near-
linear increase in the cost per query and a corresponding
increase in the demand for context-engineering techniques that
control how much input the model reads at inference. As of the
writing of this thesis, the frontier API price for a
high-end model is approximately USD~3 per million input tokens
and USD~15 per million output tokens, which corresponds to
approximately EUR~$2.76$ and EUR~$13.80$ at the time of
writing. The on-premises amortised marginal cost on a typical
mid-range GPU deployment is roughly EUR~$0.05$ per million
tokens once hardware is paid for. The two- to three-orders-of-
magnitude gap between frontier-cloud and on-premises cost is what
makes context compression an operational concern: cutting
context length by half on a frontier-cloud workload saves real
money per query.

The model-side trends are accompanied by a context-window
trend. The 2K-context GPT-2 era gave way to 4K, 8K, 32K, 128K,
and now multi-million-token contexts on the frontier. The
long-context-benchmark literature (Section~\ref{sec:rw_rag})
documents that the model's effective use of those long contexts
is less complete than the nominal window
size~\cite{liu2024lostinmiddle, hsieh2024ruler}: tokens placed in
the middle of a long context are recovered less reliably than
tokens at the start or the end. Long contexts make the case for
compression even stronger; tokens that the model will not
effectively use are pure cost.

\emph{What this thesis adds.} The model-scale trend motivates the
question that Corollary~1 of Chapter~\charef{experiments}
answers: does the cliff position depend on which point on the
model-scale curve the planner is at? The frontier validation on
Qwen-72B and DeepSeek~V4~Pro is the cross-architecture answer ---
no, within the calibrated regime --- that the scaling-era trend
makes interesting in the first place.

\section{The Cost of Running LLMs at Scale}
\label{sec:rw_cost}

The motivation chapter of this thesis frames the work in terms
of the per-token cost an operator pays. This subsection surveys
the published measurements that anchor that framing.

\paragraph{Energy.}
Luccioni, Jernite, and Strubell's 2024 \emph{Power Hungry
Processing} study~\cite{luccioni2024powerhungry} measures the
wall-power cost of inference for a broad set of open-weight
models on a single A100 GPU server. The headline number is that
text generation on a $\sim 6$B-parameter open model costs
$\sim 0.5$~Watt-hours per prompt-and-completion of typical
length, which is within an order of magnitude of the energy cost
of a single web search. The number scales near-linearly with
model size, and the per-prompt energy at frontier-scale models
(tens to hundreds of billions of parameters) is correspondingly
larger. The study also separates the per-token amortised cost
from the per-request fixed cost, and shows that for short
prompts the fixed cost dominates while for long prompts the
per-token cost dominates. The relevant implication for
compression is that the operational regime context-compression
operates in is the long-prompt regime, where the per-token cost
is what compression directly cuts.

\paragraph{Token economics.}
Industry pricing as of the writing of this thesis sits at
approximately USD~3 per million input tokens for the frontier
``base'' tier and USD~15 per million for the frontier ``output''
tier, with reasoning-augmented tiers priced higher. At a steady
state of one million calls per day and an average prompt of
$10{,}000$ tokens, that is USD~$30{,}000$ per day of input cost
alone for a frontier model. Halving the prompt length saves
USD~$15{,}000$ per day --- the kind of magnitude that funds an
entire compression-engineering team. The on-premises amortised
marginal cost is two orders of magnitude lower per token, but
the absolute hardware and operations cost of running on-
premises is high enough that the same compression lever is
operationally valuable. The TalentAdore production accounts that
this thesis's cost model is calibrated against confirm the
pricing as of the writing of the manuscript.

\paragraph{Politeness as waste.}
The industry-anecdotal observation that the compute cost of
processing user politeness at OpenAI's frontier products amounted
to ``tens of millions of dollars'' annually was made by Sam
Altman in 2025~\cite{altman2025pleasethankyou}. The exact figure
is reported as industry observation rather than as a
peer-reviewed measurement; the direction is consistent with the
Luccioni numbers~\cite{luccioni2024powerhungry} and is plausible
on a back-of-the-envelope. Every ``Hello'', ``Thanks'', restated
history, and repeated system prompt is converted directly into
kilowatt-hours and dollars. The thesis uses the framing as the
opening rhetorical hook (Chapter~\charef{introduction}); the
substantive question of how aggressively the wasted tokens can be
removed without losing the answer is what the rest of the thesis
measures.

\paragraph{Multi-agent multiplier.}
Anthropic's report on their multi-agent research
system~\cite{anthropic2025multiagent} observes that token usage
explains approximately $80\%$ of the performance variance they
see, and that a substantial fraction of that token cost is the
shared context that flows between agents in each round. The
follow-on report on context engineering for AI
agents~\cite{anthropic2025contextengineering} and the report on
context editing and memory tools~\cite{anthropic2025contextediting}
describe an $84\%$ token reduction on a 100-turn web-search
evaluation. These are industry observations rather than
controlled measurements; what they do is establish that the
cost-of-context question is operationally pressing for production
multi-agent deployments.

\emph{What this thesis adds.} Prior work establishes that
inference cost is real, that compression cuts it, and that
deployed multi-agent systems are dominated by token cost. What is
missing is the structural answer to \emph{how aggressively
compression can be applied before coordination breaks}. The cliff
characterisation of Chapter~\charef{experiments} is that answer.

\section{Context Compression --- the Breakthrough Works}
\label{sec:rw_compression}

The training-free context-compression literature has matured in
the past three years into four recognisable families. This
subsection surveys the four, with a comparison table at the end
that maps the families against the design dimensions that matter
for multi-fragment evaluation. Each family closes with a
``what is missing in prior work'' line that the rest of the
thesis addresses.

\subsection{Token-level pruning (the LLMLingua family)}

The first practical context-compression technique to see broad
adoption was LLMLingua~\cite{jiang2023llmlingua}, which uses a
small autoregressive language model to score tokens by their
per-step perplexity contribution and drop those whose removal
least disturbs the conditional distribution. LongLLMLingua
\cite{jiang2024longllmlingua} extends the coarse-to-fine ranking
with a question-aware step to handle long retrieval-augmented
contexts. LLMLingua-2~\cite{pan2024llmlingua2} trains an
XLM-RoBERTa token classifier on data distilled from a more
capable model, producing a task-agnostic compressor that is
faster at inference than the original LLMLingua because it does
not require running a generative model at compression time. The
LLMLingua-2 classifier is the principal hard-prompt compressor of
this thesis; its evaluation centres on NarrativeQA F1
within $2$~pp and HotpotQA F1 within $3$~pp of reported
numbers~\cite{kocisky2018narrativeqa, yang2018hotpotqa} as the
calibration target.

\emph{What is missing in prior work.} All three LLMLingua papers
report single-agent question-answering F1 retention at modest
compression ratios. None measures whether the surviving content
is sufficient for a downstream planner to combine information
across multiple compressed fragments into a correct answer. H1
of Chapter~\charef{experiments} measures exactly that and
finds that the single-agent F1 metric does not predict
coordination success.

\subsection{Selective and instruction-aware compression}

Li \emph{et~al.}'s \emph{Selective
Context}~\cite{li2023selective} prunes tokens
with low self-information under the model's own conditional
distribution; the technique requires no training but does
require running a scoring forward-pass at compression time. Xu
\emph{et~al.}'s \emph{RECOMP}~\cite{xu2024recomp} compresses long retrieval contexts
with a small task-aware extractor trained to summarise the
retrieved passages for the downstream question. The
instruction-aware filter of this thesis sits in the same family
but takes the deliberate simplification of using a TF-IDF
pruning step followed by a cross-encoder re-ranker
(\texttt{BAAI/bge-reranker-base}) and a stop-word/short-token
trim, with no LM in the loop. The simplification gives a
deterministic, training-free, low-cost baseline that the more
sophisticated compressors must beat.

\emph{What is missing in prior work.} The task-awareness in this
literature is question-conditioned: the compressor takes the
downstream question as input and prunes against it. In a
multi-fragment workflow the planner's question is not the
fragment-level task; the fragment-level task is to preserve
information that a planner-as-yet-unknown will combine with
information from other fragments. The thesis's
instruction-aware filter and the empirical evaluation of all
four compressors on multi-fragment families address this gap.

\subsection{Learned compression (parameter-cost compressors)}

Mu \emph{et~al.}~\cite{mu2023gist} introduced \emph{gist tokens},
special positions trained with a masked attention pattern so that
the model learns to compress instruction prefixes into a small
number of virtual tokens. Chevalier
\emph{et~al.}~\cite{chevalier2023autocompressor} extended this
with \emph{AutoCompressor}, which fine-tunes a language model to
process long documents segment by segment and produce summary
vectors. Ge \emph{et~al.}~\cite{ge2024icae} formalised the
architecture as the \emph{In-context Autoencoder (ICAE)}, which
trains a LoRA-adapted encoder to produce a fixed number of
memory tokens from an input context. Wang
\emph{et~al.}~\cite{wang2024icf} present the In-Context Former,
a faster cross-attention variant. Rae
\emph{et~al.}~\cite{rae2020compressive} introduced the
Compressive Transformer architecture, which is the closest
single-context analogue of the cliff bound this thesis derives.

\emph{What is missing in prior work.} The learned-compression
papers require training, which introduces both a training-data
asymmetry between compressors (which makes cross-compressor
comparison less clean) and an operational deployment cost (every
new compressor needs its own fine-tune). This thesis deliberately
stays training-free; the LLMLingua-2 wrapper, the
instruction-aware filter, the Phi-3-Mini extractive span
selector, and the truncation baseline are all inference-only,
which makes the cliff comparison turn on the
algorithm-of-action rather than on training-budget asymmetry.
The learned-compression literature could be re-evaluated under
the multi-fragment cliff methodology of this thesis as a
follow-on study; the thesis does not do so directly.

\subsection{Extractive small-LLM span selection}

Recent work uses small instruction-tuned LLMs as extractive
compressors that produce verbatim spans of the source rather than
abstractive summaries. The candidate small LLMs are the Phi-3
family~\cite{phi3} and other $\sim 3$B-parameter instruction-tuned
models. Extractive compression is privacy-friendly because the
compressed output is by construction a subset of the source
tokens; this is one of the reasons it appears in this thesis as
a compressor option.

\emph{What is missing in prior work.} The published guidance on
how to enforce the extractive constraint reliably is thin; small
LLMs frequently insert function-word filler even when told not
to. The Phi-3-Mini extractive compressor of this thesis ships a
post-hoc verifier with a $15\%$ novel-token tolerance and an
LLMLingua-2 fallback that together salvage outputs whose
extractive fraction is above $50\%$; the architecture is
documented in detail in
Section~\ref{sec:compressors} of Chapter~\charef{implementation}
and is one of the engineering contributions of the thesis.

\subsection{Comparison table}

\begin{table}[h]
\centering
\caption{The compressor families this thesis surveys, along the
design dimensions that matter for multi-fragment evaluation. The
third column is the property H1 of Chapter~\charef{experiments}
turns on: no prior compressor was evaluated on a controlled
multi-fragment coordination sweep before this thesis.}
\label{tab:rw_comparison}
\small
\begin{tabular}{p{4.5cm}p{2cm}p{2cm}p{2cm}p{2.5cm}}
\hline
Family & Training\hspace*{0pt}-free? & Task\hspace*{0pt}-aware? & Eval'd on multi\hspace*{0pt}-fragment? & Deployed in this thesis? \\
\hline
LLMLingua family~\cite{jiang2023llmlingua, jiang2024longllmlingua, pan2024llmlingua2} & yes (inference-only) & question-conditioned & no & LLMLingua-2 \\
Selective Context, RECOMP & yes & yes & no & --- \\
Gist Tokens / AutoCompressor / ICAE~\cite{mu2023gist, chevalier2023autocompressor, ge2024icae} & no (training required) & varies & no & --- \\
Extractive small-LLM (Phi-3 family)~\cite{phi3} & yes (inference-only) & yes & no & Phi-3-Mini ext. \\
Instruction-aware filter & yes & yes & no & yes (this thesis) \\
Truncation (prefix-keep) & yes & no & no & yes (baseline) \\
\hline
\textbf{This thesis (multi-fragment cliff sweep)} & \textbf{yes} & \textbf{yes} & \textbf{yes} & \textbf{four compressors} \\
\hline
\end{tabular}
\end{table}

\section{Multi-Agent LLM Systems and Agentic Memory}
\label{sec:rw_multiagent}

The multi-agent LLM-systems literature has grown rapidly since
2023. The most-cited frameworks are
AutoGen~\cite{wu2023autogen} (an open-source framework for
multi-agent conversation; appeared at the ICLR 2024 LLM-Agents
Workshop rather than as a main-conference paper),
MetaGPT~\cite{hong2024metagpt} (ICLR 2024 main),
CAMEL~\cite{li2023camel} (NeurIPS 2023),
Reflexion~\cite{shinn2023reflexion} (NeurIPS 2023),
MemGPT~\cite{packer2023memgpt} (preprint, not yet
peer-reviewed at the time of writing of this thesis), and
Generative Agents~\cite{park2025collaborative} (UIST 2023). Each
framework has its own implicit answer to the question of how
shared context flows between agents and what an individual agent
needs to see. None of the frameworks formally bounds the
information loss introduced when that shared context is
compressed.

The agentic-memory line of work
\cite{packer2023memgpt, xu2025amem, chhikara2025mem0,
rasmussen2025zep, saleh2025memindex, saleh2025messagebrokers}
addresses the related question of how to store and retrieve
agent state across long horizons. The closest published academic
analogue to this thesis's memory bus is
MemIndex~\cite{saleh2025memindex}, which the three-layer memory-
bus architecture of Chapter~\charef{implementation} explicitly
extends. The MemGPT-style ``LLM as operating system''
framing~\cite{packer2023memgpt} is related but is concerned with
single-agent long-horizon memory rather than multi-agent shared
state. Mem0~\cite{chhikara2025mem0} is a production-oriented
agentic-memory service.

\emph{What is missing in prior work.} The multi-agent and
agentic-memory frameworks treat compression as an implicit
deployment optimisation; none measures the \emph{multi-fragment}
coordination-quality cost of compression structurally or bounds
the loss quantitatively. This thesis fills the multi-fragment
measurement gap directly (the cliff sweep,
Section~\ref{sec:h2}, and the inference-disclosure measurement,
Section~\ref{sec:h4_disclosure}); it does \emph{not} fill the
multi-round-agent measurement gap, which the AutoGen backend in
\texttt{src/m6/orchestrator/} is positioned to address as future
work (ADR-009; Section~\ref{sec:future}). The memory bus of
Chapter~\charef{implementation} is designed as the reference
target for both, but the empirical evidence in this thesis is
multi-fragment, not multi-round.

\section{Retrieval-Augmented Generation and Long-Context Benchmarks}
\label{sec:rw_rag}

Retrieval-augmented generation as a paradigm dates to Lewis
\emph{et~al.}~\cite{lewis2020rag}. The landmark works since
include RAPTOR~\cite{sarthi2024raptor} (recursive abstractive
processing for tree-organised retrieval, ICLR 2024),
GraphRAG~\cite{edge2024graphrag} (a Microsoft preprint at the
time of writing, not yet at a peer-reviewed venue),
HippoRAG~\cite{gutierrez2024hipporag, gutierrez2025hipporag2}
(NeurIPS 2024 and follow-on), and
Self-RAG~\cite{asai2024selfrag} (ICLR 2024). The pipeline
catalogue this thesis evaluates (P1, P2, P3) places compression
on the retrieval critical path explicitly; the closest published
analogue to the post-retrieval-compression pipeline (P2) is the
LongLLMLingua configuration~\cite{jiang2024longllmlingua}, and
the closest published analogue to the joint
relevance-conditional pipeline (P3) is the dynamic-routing
framework of Guo \emph{et~al.}~\cite{guo2025dynamic}.

The long-context-benchmark literature
(\cite{bai2024longbench, hsieh2024ruler, liu2024lostinmiddle,
mialon2023gaia, liu2024agentbench, yen2025helmet}) measures how
effectively a model uses a long context. The
``lost in the middle'' result~\cite{liu2024lostinmiddle} is the
canonical observation that information placed in the middle of a
long context is recovered less reliably than information at the
boundaries. RULER~\cite{hsieh2024ruler} extends the
needle-in-a-haystack methodology to a broader set of long-context
tasks. LongBench~\cite{bai2024longbench} is the standard
multi-task benchmark. None of these benchmarks measures the
multi-fragment-coordination task structure of this thesis;
they measure single-agent long-context comprehension. They are
complementary to the cliff measurement rather than competitive
with it: long-context benchmarks measure the capacity of the
model, while the cliff measurement measures the compression-
quality effect on a task structure the long-context benchmarks
do not include.

The multi-hop question-answering benchmarks
HotpotQA~\cite{yang2018hotpotqa} (EMNLP 2018),
2WikiMultiHopQA~\cite{ho2020wiki2hop} (COLING 2020), and
MultiHopRAG~\cite{tang2024multihoprag} (Findings of EMNLP 2024)
are the real-data benchmarks on which Corollary~2 of
Chapter~\charef{experiments} validates the
information-density-scaling claim. The transfer is
qualitative: the absolute cliff positions differ between
synthetic and real benchmarks because the information density
$\theta_\text{info}$ differs, but the cliff structure
(existence, sharpness as a function of $\theta_\text{info}$)
transfers.

\emph{What is missing in prior work.} The RAG and long-context
benchmark literatures measure orthogonal properties to this
thesis. The cliff measurement complements them rather than
competing: RAG benchmarks measure retrieval quality, long-context
benchmarks measure model capacity, and the cliff measurement
measures the multi-fragment compression-quality effect that
neither captures. The H3 catalogue of three RAG-plus-compression
pipelines under matched cost regimes fills the
compression-on-the-retrieval-critical-path measurement gap.

\section{Privacy in Agentic Memory and Compressed Retrieval}
\label{sec:rw_privacy}

The privacy-aware-retrieval literature has two strands.
The first protects the retrieval index itself, on the assumption
that direct access to the index would leak protected facts.
Examples include PrivacyRAG~\cite{zhou2025privacyrag} and
SecureRAG~\cite{bassit2025securerag}. The second strand protects
the model weights from training-data extraction, which is a
property of the training pipeline rather than of the deployed
retrieval-and-compression service.

The inference-disclosure metric this thesis contributes (C4) is
distinct from both: it measures leakage \emph{through the
compressor itself}, on the assumption that the retrieval index
is access-controlled but the compressed summaries are exposed to
the planner and to any downstream reader the planner shares them
with. The threat model is intuitive: an adversary who can query
the planner can ask questions about the protected fact, and the
disclosure rate is the fraction of those questions on which the
planner's answer recovers the protected fact given that it has
the compressed summary as evidence. The H4 measurement
operationalises this in a controlled setup; the memory-bus
policy layer of Chapter~\charef{implementation} operationalises
the resulting disclosure budget as a deployment-time enforcement
mechanism.

The CFedRAG framework~\cite{addison2024cfedrag} is a related
piece of work on coordination of federated retrieval-augmented
generation; it addresses the retrieval-index-level privacy
question rather than the compressor-level disclosure question
that this thesis takes up.

\emph{What is missing in prior work.} No published academic
work, to the author's knowledge, measures inference disclosure
through the compressor at the summary level. Privacy-aware
retrieval protects the index; this thesis protects the summary.
The two are complementary, and a future system would presumably
combine them.

\section{The Gap This Thesis Closes}
\label{sec:rw_gap}

Four sentences, each one mapping to one of the four contributions
of Chapter~\charef{introduction}.

There is no shared multi-fragment coordination benchmark
probing the cliff in a controlled, reproducible setup. C1 is the
benchmark.

There is no published operational bound that predicts cliff
position from compressor-side and task-side measurements within
a defined regime. The compounding-error model and its
cross-architecture frontier validation are the bound.

There is no honest catalogue of RAG-plus-compression pipeline
placement under matched cost regimes, with the cost model
explicit in EUR per workflow. The C3 catalogue is the
catalogue, and its honest finding is that the assumed
sign-flip does not appear.

There is no published academic measurement of inference
disclosure through the compressor at the summary level. The H4
measurement, integrated with the memory bus's policy layer, is
the measurement.

The closest published industry analogue to C2 is Anthropic's
multi-agent system report~\cite{anthropic2025multiagent},
labelled honestly as industry observation rather than
controlled measurement. The closest published academic analogues
are the long-context benchmark suite and the LLMLingua line of
work, which measure orthogonal properties on the single-agent
axis. The thesis sits at the intersection of these three
threads, and contributes the controlled cross-compressor
multi-fragment evaluation that the prior work does not provide.
