This chapter draws together the thesis as it stands at submission. The
empirical narrative that connects the eight hypotheses, the quantitative
findings, and the comparison against the falsification targets is the
content of the discussion proper, and will be inserted here once the
experimental runs of Months~3, 4, 6, 7, and~8 have finished and the
verdicts are in. The structure of the discussion is fixed: the chapter
revisits the four contributions in order, summarises the empirical
findings or reports the falsifications, then moves to the limitations,
the deliverables, the doctoral-phase bridge, and the closing remarks.

% RESULTS: Insert the empirical-findings prose here once H1-H8 verdicts are in.
%          The skeleton below is the structure the prose will populate; each
%          paragraph is a placeholder.

\section{Summary of Empirical Findings}
\label{sec:findings}

% RESULTS: One paragraph per hypothesis, in the H1-H8 order. Each paragraph
%          states the falsifiable claim, the verdict (supported / falsified /
%          inconclusive), the headline effect size with its bootstrap CI, and
%          a short interpretive sentence connecting back to the narrative arc
%          of Chapter 1. Where a verdict is "falsified", the paragraph
%          explicitly names the falsification as a thesis-worthy finding per
%          the implementation-plan stance.

\paragraph{H1.} % to be inserted from results/h1/.../verdicts.json
\paragraph{H2.} % to be inserted from results/h2/.../verdicts.json
\paragraph{H3.} % to be inserted from results/h3/.../verdicts.json
\paragraph{H4.} % to be inserted from results/h4/.../verdicts.json
\paragraph{H5.} % to be inserted from results/h5/.../verdicts.json
\paragraph{H6.} % to be inserted from results/h6/.../verdicts.json
\paragraph{H7.} % to be inserted from results/h7/.../verdicts.json
\paragraph{H8.} % to be inserted from results/h8/.../verdicts.json (or deferred)

\section{Stretch Goals}
\label{sec:stretch}

The implementation plan reserves Month~8 for at most two stretch goals
selected at the end of Month~7 from a pre-agreed list:

\begin{description}\setlength\itemsep{0pt}
\item[S1 --- Calibration study.] Fit the piecewise-linear cliff on
$\leq 100$ workload instances and use it to predict $\tau^{*}$ on
held-out workflows. Target mean absolute error of at most $1.5$ ratio
units. Adds a practical-deployability section to
Chapter~\charef{experiments}.

\item[S2 --- Adversarial robustness.] A SecurityLingua-style red-team
sweep against the tag-preserving compressor~\cite{li2025securitylingua}.
Reports tag-preservation under adversarial prompts. Hardens the C4
governance claims.

\item[S3 --- Haseeb baseline.] Implement the multi-agent context-
engineering approach of Haseeb~\cite{haseeb2025contextengineering} as
a baseline comparator on C1 against the C2 compressor suite. Strengthens
Chapter~\charef{relatedwork}.

\item[S4 --- TalentAdore trace replication.] With Asim Nadeem and Oskari
Valkama, replicate the C1 evaluation on an NDA-cleared TalentAdore
production trace. Strengthens the industry-relevance arm.

\item[S5 --- Compression and market mechanism.] Feed compression ratio
into the polymatroid simulation harness of Paper~1~\cite{loven2025paper1}
and report welfare under compression. Cleanest bridge to the doctoral-
phase mechanism-design work.
\end{description}

% RESULTS-STRETCH: The two selected stretch goals' results will be inserted
%                  here. The selection itself is taken at the end of Month 7
%                  based on Lauri's input.

\section{Limitations}
\label{sec:limitations}

\paragraph{Synthetic benchmark.} The C1 benchmark is synthetic. The H8
arm is the construct-validity counterweight, but the documented-as-
deferred path is honest about the possibility that no M0/M1/M2 trace is
ready by Month~7. The synthetic-to-real transfer evidence will be as
strong as the agents that are ready when the experiments run.

\paragraph{Single workstation.} All training and evaluation fit a single
Apple M4 Pro 48~GB workstation. The 70B int4 result is a
\emph{single-point} characterisation, not a sweep; it relies on the
NarrativeQA-shaped sanity check passing at startup, and the manuscript is
explicit about this dependency.

\paragraph{Tag-preserving compressor as a research prototype.} The
tag-preserving compressor is a research prototype with measured
properties, not a compliance tool. It is not certified against any
particular ACL or governance framework. The use of the NIST
AI~RMF~\cite{nistairmf} lattice in the tag vector borrows only the
vocabulary.

\paragraph{Statistical power.} Five seeds per cell gives modest power
for very small effect sizes. The Holm-Bonferroni correction is
conservative on hypothesis families with many members. The thesis
chooses both anyway: the alternative (under-correcting and
over-reporting) would be worse for a manuscript that the doctoral phase
has to build on.

\paragraph{Audit log.} The tamper-evident hash chain in the audit log
detects in-process tampering but does not defend against file-level
attacks on the SQLite database. This is the explicit subject of
ADR-005 in the technical reference and is deferred to the doctoral phase
for hardening via cryptographic commitment.

\paragraph{Agent runtime version pinning.} AutoGen v0.4 is pinned. A
minor-version bump during the thesis window could change behaviour;
the pinning is the documented mitigation and the no-compression
control condition is the second.

\section{Bridge to Doctoral Research (D7)}
\label{sec:d7}

The thesis is the substrate for doctoral track~7 (Federated Knowledge
Orchestration). The four artefacts feed forward as follows:

\paragraph{Working benchmark.} The C1 benchmark is extensible to real-
system traces (the H8 arm is the gentle on-ramp), to cross-institutional
federation (D7's territory), and to richer adversarial governance
scenarios (S2 hardening).

\paragraph{Empirical baseline.} The C2 characterisation gives D7 a
single-institution reference against which federated, cross-tokenizer,
or larger-institutional measurements can be compared.

\paragraph{RAG pipeline catalogue.} C3 is scaffolding for cross-
institutional retrieval under bandwidth and privacy budgets. P3's
score-conditional routing generalises naturally to a federated setting
in which the relevance threshold becomes a per-institution policy
variable.

\paragraph{Memory-bus integration.} The C4 reference memory-bus
integration is the contract D7 picks up. The doctoral phase replaces
SQLite with Postgres, the in-memory scratchpad with Redis Cluster, FAISS
with Qdrant, the HTTP interface with NATS plus Kafka, and the hash chain
with the cryptographic commitment infrastructure of
Paper~2~\cite{loven2025paper2} and Paper~3~\cite{loven2025paper3}. The
storage-protocol seams documented in Chapter~\charef{implementation} are
designed for that substitution.

The four doctoral-phase sub-questions the master's-scale work does not
answer but its scaffolding makes tractable are: how the coordination
cliff shifts under federation latency; whether tag-preservation rates
survive federated aggregation; what governance properties the
cryptographic commitment scheme adds over per-slot tags; and how C1
extends to a cross-institutional benchmark suite with the governance
constraints that federated settings impose. These sit waiting for D7
and define the boundary at which the master's-scale work ends.

\section{Deliverables}
\label{sec:deliverables}

The thesis is delivered together with: the open-source reference
implementation hosted on GitHub at a release tag matching the manuscript
version, the C1 benchmark v0.1 reproducible from a single command, the
tag-preserving compressor weights released on the HuggingFace hub with
model and data cards, a Docker compose deployment for the memory-bus
service, and a one-command reproduction target for each chapter-headline
figure (\texttt{make reproduce-ch\{5..8\}}). The reproducibility package
is the final deliverable; the manuscript is the second-final.

\section{Closing}
\label{sec:closing}

% RESULTS: Closing paragraph to be inserted once the empirical-findings
%          section is populated. The closing should restate the empirical
%          headline (the coordination cliff result), connect it to the
%          plan's narrative arc, and acknowledge the limitations honestly.
